### 2016-06-20 paper.tex
Authors and title

%"runningheads" enables:
%  - page number on page 2 onwards
%  - title/authors on even/odd pages
%This is good for other readers to enable proper archiving among other papers and pointing to content.
%Even if the title page states the title, when printed and stored in a folder, when blindly opening the folder, one could hit not the title page, but an arbitrary page. Therefore, it is good to have title printed on the pages, too.
\documentclass[runningheads,a4paper]{llncs}

%Even though `american`, `english` and `USenglish` are synonyms for babel package (according to https://tex.stackexchange.com/questions/12775/babel-english-american-usenglish), the llncs document class is prepared to avoid the overriding of certain names (such as "Abstract." -> "Abstract" or "Fig." -> "Figure") when using `english`, but not when using the other 2.
\usepackage[english]{babel}

%better font, similar to the default springer font
%cfr-lm is preferred over lmodern. Reasoning at http://tex.stackexchange.com/a/247543/9075
\usepackage[%
rm={oldstyle=false,proportional=true},%
sf={oldstyle=false,proportional=true},%
tt={oldstyle=false,proportional=true,variable=true},%
qt=false%
]{cfr-lm}
%
%if more space is needed, exchange cfr-lm by mathptmx
%\usepackage{mathptmx}

\usepackage{graphicx}

%extended enumerate, such as \begin{compactenum}
\usepackage{paralist}

%put figures inside a text
%\usepackage{picins}
%use
%\piccaptioninside
%\piccaption{...}
%\parpic[r]{\includegraphics ...}
%Text...

%Sorts the citations in the brackets
%\usepackage{cite}

\usepackage[T1]{fontenc}

%for demonstration purposes only
\usepackage[math]{blindtext}

%for easy quotations: \enquote{text}
\usepackage{csquotes}

%enable margin kerning
\usepackage{microtype}

%tweak \url{...}
\usepackage{url}
%nicer // - solution by http://tex.stackexchange.com/a/98470/9075
\makeatletter
\def\Url@twoslashes{\mathchar`\/\@ifnextchar/{\kern-.2em}{}}
\g@addto@macro\UrlSpecials{\do\/{\Url@twoslashes}}
\makeatother
\urlstyle{same}
%improve wrapping of URLs - hint by http://tex.stackexchange.com/a/10419/9075
\makeatletter
\g@addto@macro{\UrlBreaks}{\UrlOrds}
\makeatother

%diagonal lines in a table - http://tex.stackexchange.com/questions/17745/diagonal-lines-in-table-cell
%slashbox is not available in texlive (due to licensing) and also gives bad results. This, we use diagbox
%\usepackage{diagbox}

%required for pdfcomment later
\usepackage{xcolor}

% new packages BEFORE hyperref
% See also http://tex.stackexchange.com/questions/1863/which-packages-should-be-loaded-after-hyperref-instead-of-before

%enable hyperref without colors and without bookmarks
\usepackage[
%pdfauthor={},
%pdfsubject={},
%pdftitle={},
%pdfkeywords={},
bookmarks=false,
breaklinks=true,
colorlinks=true,
linkcolor=black,
citecolor=black,
urlcolor=black,
%pdfstartpage=19,
pdfpagelayout=SinglePage,
pdfstartview=Fit
]{hyperref}
%enables correct jumping to figures when referencing
\usepackage[all]{hypcap}

%enable nice comments
\usepackage{pdfcomment}
\newcommand{\commentontext}[2]{\colorbox{yellow!60}{#1}\pdfcomment[color={0.234 0.867 0.211},hoffset=-6pt,voffset=10pt,opacity=0.5]{#2}}
\newcommand{\commentatside}[1]{\pdfcomment[color={0.045 0.278 0.643},icon=Note]{#1}}

%compatibality with TODO package
\newcommand{\todo}[1]{\commentatside{#1}}

%enable \cref{...} and \Cref{...} instead of \ref: Type of reference included in the link
\usepackage[capitalise,nameinlink]{cleveref}
%Nice formats for \cref
\crefname{section}{Sect.}{Sect.}
\Crefname{section}{Section}{Sections}

\usepackage{xspace}
%\newcommand{\eg}{e.\,g.\xspace}
%\newcommand{\ie}{i.\,e.\xspace}
\newcommand{\eg}{e.\,g.,\ }
\newcommand{\ie}{i.\,e.,\ }

%introduce \powerset - hint by http://matheplanet.com/matheplanet/nuke/html/viewtopic.php?topic=136492&post_id=997377
\DeclareFontFamily{U}{MnSymbolC}{}
\DeclareSymbolFont{MnSyC}{U}{MnSymbolC}{m}{n}
\DeclareFontShape{U}{MnSymbolC}{m}{n}{
    <-6>  MnSymbolC5
   <6-7>  MnSymbolC6
   <7-8>  MnSymbolC7
   <8-9>  MnSymbolC8
   <9-10> MnSymbolC9
  <10-12> MnSymbolC10
  <12->   MnSymbolC12%
}{}
\DeclareMathSymbol{\powerset}{\mathord}{MnSyC}{180}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

%Works on MiKTeX only
%hint by http://goemonx.blogspot.de/2012/01/pdflatex-ligaturen-und-copynpaste.html
%also http://tex.stackexchange.com/questions/4397/make-ligatures-in-linux-libertine-copyable-and-searchable
%This allows a copy'n'paste of the text from the paper
\input glyphtounicode.tex
\pdfgentounicode=1

\title{Collecting operator-client conversation aligned with knowledge-base queries}
%If Title is too long, use \titlerunning
%\titlerunning{Short Title}

%Single insitute
\author{Ond\v{r}ej Pl\'{a}tek \and Filip Jur\v{c}\'{i}\v{c}ek}
%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}
\institute{Charles University in Prague, Faculty of Mathematics and Physics}

%Multiple insitutes
%Currently disabled
%
\iffalse
%Multiple institutes are typeset as follows:
\author{Firstname Lastname\inst{1} \and Firstname Lastname\inst{2} }
%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}

\institute{
Insitute 1\\
\email{...}\and
Insitute 2\\
\email{...}
}
\fi

\maketitle

\begin{abstract}
    This paper presents a datasets which contains task oriented conversation between an operator, a task expert, and a client who is seeking information about the task.
    The dataset was collected to be used for training end-to-end task oriented conversational agents just from conversations with and KB-calls from the operator.
\end{abstract}

\keywords{...}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blindtext\todo{Refine me}

Winery~\cite{Winery} is graphical \commentontext{modeling}{modeling with one \enquote{l}, because of AE} tool.

\begin{figure}
Simple Figure
\caption{Simple Figure}
\label{fig:simple}
\end{figure}

\begin{table}
\caption{Simple Table}

\label{tab:simple}
Simple Table
\end{table}

cref Demonstration: Cref at beginning of sentence, cref in all other cases.

\Cref{fig:simple} shows a simple fact, although \cref{fig:simple} could also show something else.

\Cref{tab:simple} shows a simple fact, although \cref{tab:simple} could also show something else.

\Cref{sec:intro} shows a simple fact, although \cref{sec:intro} could also show something else.

Brackets work as designed:
<test>

The symbol for powerset is now correct: $\powerset$ and not a Weierstrass p ($\wp$).

\begin{inparaenum}
\item All these items...
\item ...appear in one line
\item This is enabled by the paralist package.
\end{inparaenum}

``something in quotes'' using plain tex or use \enquote{the enquote command}.

\section{Conclusion and Outlook}

\subsubsection*{Acknowledgments}
...

In the bibliography, use \texttt{\textbackslash textsuperscript} for ``st'', ``nd'', ...:
E.g., \enquote{The 2\textsuperscript{nd} conference on examples}.
When you use \href{http://www.jabref.org}{JabRef}, you can use the clean up command to achieve that.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{splncs03}
\bibliography{paper}

All links were last followed on October 5, 2014.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2016-06-21 paper.tex
first version abstract

@@
 %This is good for other readers to enable proper archiving among other papers and pointing to content.
-%Even if the title page states the title, when printed and stored in a folder, when blindly opening the folder, one could hit not the title page, but an arbitrary page.
-Therefore, it is good to have title printed on the pages, too.
-\documentclass[runningheads,a4paper]{llncs}
 
@@
 %Single insitute
+TODO ANONYMIZE
 \author{Ond\v{r}ej Pl\'{a}tek \and Filip Jur\v{c}\'{i}\v{c}ek}
@@
 %\authorrunning{First Author et al.}
-\institute{Charles University in Prague, Faculty of Mathematics and Physics}
+\institute{Charles University in Prague, Faculty of Mathematics and Physics \\
+Insitute of Formal and Applied Linguistics \\
+Malostransk\'{e} n\'{a}m\v{e}st\'i 25, 11800 Praha 1, Czech Republic \\
+\email{\{oplatek,jurcicek\}@ufal.mff.cuni.cz}}
 
@@
 \begin{abstract}
-    This paper presents a datasets which contains task oriented conversation between an operator, a task expert, and a client who is seeking information about the task.
-    The dataset was collected to be used for training end-to-end task oriented conversational agents just from conversations with and KB-calls from the operator.
+    This paper presents a novel datasets for for training end-to-end task oriented conversational agents.
+    The dataset contains task oriented conversation between an operator, a task expert, and a client who is seeking information about the task along with records of data base API calls of the operator, which capture the distilled meaning of the user query.
+    The data base calls represent not only instantiation of user wishes but also, when evaluated against the database determine the answer from the database, which were used by the operator to provide requested information to the client.
+    We expect that this additional supervision of recording database interaction will provide enough information so the task of the conversation can be understood and behaviour of the interlocutors reconstructed by software agents.
+    The dataset was collected using crowdsourcing in offline setting, where each contributor played role either of an operator or a client and contributed single utterance.
+    The quality of the data were enforced by mutual control among contributors and manually verified on random sub-sample.
+    The dataset is available for download under the Creative Commons 4.0 BY-SA license.
 \end{abstract}
 
-\keywords{...}
+\keywords{task-oriented dialogue, end-to-end, dataset}
 

### 2016-06-21 paper.tex
intro draft, named section

@@
 %Even though `american`, `english` and `USenglish` are synonyms for babel package (according to https://tex.stackexchange.com/questions/12775/babel-english-american-usenglish), the llncs document class is prepared to avoid the overriding of certain names (such as "Abstract." -> "Abstract" or "Fig." -> "Figure") when using `english`, but not when using the other 2.
+\documentclass[runningheads,a4paper]{llncs}
 \usepackage[english]{babel}
@@
 
-%Single insitute
-TODO ANONYMIZE
-\author{Ond\v{r}ej Pl\'{a}tek \and Filip Jur\v{c}\'{i}\v{c}ek}
-%If there are too many authors, use \authorrunning
-%\authorrunning{First Author et al.}
-\institute{Charles University in Prague, Faculty of Mathematics and Physics \\
-Insitute of Formal and Applied Linguistics \\
-Malostransk\'{e} n\'{a}m\v{e}st\'i 25, 11800 Praha 1, Czech Republic \\
-\email{\{oplatek,jurcicek\}@ufal.mff.cuni.cz}}
+% %Single insitute
+% \author{Ond\v{r}ej Pl\'{a}tek \and Filip Jur\v{c}\'{i}\v{c}ek}
+% %If there are too many authors, use \authorrunning
+% %\authorrunning{First Author et al.}
+% \institute{Charles University in Prague, Faculty of Mathematics and Physics \\
+% Insitute of Formal and Applied Linguistics \\
+% Malostransk\'{e} n\'{a}m\v{e}st\'i 25, 11800 Praha 1, Czech Republic \\
+% \email{\{oplatek,jurcicek\}@ufal.mff.cuni.cz}}
 
@@
 %
-\iffalse
+% \iffalse % FIXME enable for blind review and ucomment Single institute with filled values 
+\iftrue % FIXME enable for blind review and ucomment Single institute with filled values 
 %Multiple institutes are typeset as follows:
@@
 \begin{abstract}
-    This paper presents a novel datasets for for training end-to-end task oriented conversational agents.
+    This paper presents a novel datasets for training end-to-end task oriented conversational agents.
     The dataset contains task oriented conversation between an operator, a task expert, and a client who is seeking information about the task along with records of data base API calls of the operator, which capture the distilled meaning of the user query.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blindtext\todo{Refine me}
+We present a new dataset of human-human task-oriented conversation in domain of Cambridge restaurant services targeted for supervised training of autonomous systems to play role of the operator which provides information about the restaurants to clients.
+In contrast to previously released datasets, our datasets contains easy to obtain high-quality transcriptions of the client and operator actions during conversations.
+We introduce a~very little overhead by collecting data base calls in addition to the transcription of the conversation. 
+In fact, we mimic very closely a~real situation in call centers where operators searches for answers through database user interface. 
+On the other hand, just logging the calls to the task database provide us with information of the similar quality as it is contained in manually annotated dialogue state, just not annotated incrementally after each turn.
+Tracking the database calls in task oriented systems together with conversation transcription should not introduce much overhead during data collection, but should presumably boost end-to-end conversational agent as much as annotated dialogue state when training with such data.
 
-Winery~\cite{Winery} is graphical \commentontext{modeling}{modeling with one \enquote{l}, because of AE} tool.
+Current Spoken Dialogue Systems (SDS) are either handcrafted and use no training data\cite{alex},\cite{todo}, but require non-trivial amount of expert work, or are gradually improved from initial policy through live user interaction\cite{Pomdp-young,gasix}, and lately are trained using supervised learning typically in end-to-end manner\cite{Wen2016,Williams2016}.\footnote{The~work of \cite{Williams2016} also fine tuned the conversation with reinforcement learning after the supervised-learning stage.}
+The reinforce learning on one hand need just collect enough live user conversation without any transcription with the exception of explicit feedback at the end of each dialogue, but because the feedback signal is typically rather noise and delayed one require thousands of live conversations to improve rather simple policy.\cite{gasic}
+The supervised-learning methods greatly reduced the number of conversation needed for training reasonable policy to few hundreds\cite{Wen2016}, but require annotation for all components used the dialogue which so far included at least a dialogue state\cite{Wen, his}.
+Since the dialogue state is simplification of dialogue history and has no broadly-accepted form, it is very expensive to collect such annotated data because the dialogue state typically differs among domains and its structure is hard to explain to annotators.
+In this paper, we focus on collecting supervised training set with rich enough annotation so the supervised models similar to~\cite{Wen2016} can be trained with few hundreds of dialogues, but the annotation of dialogues are much easier to collect.
+
+We believe that the present dataset can be used for first experiments for end-to-end systems using supervised learning without annotated dialogue state.
+The resulting systems should be able to roughly compare to systems trained on datasets with \cite{dstsc2, dstc3} dialogue state annotation because the same settings, i.e.\ database and task, for data collection.
+Despite the fact, we collected human-to-human dialogues on known task of Cambridge restaurant domains the data-collecting method is completely domain and language independent.
+
+The paper is structured as follows:
+XY
 
@@
 
-cref Demonstration: Cref at beginning of sentence, cref in all other cases.
+\section{End-to-end training of dialogue systems}
+\label{sec:training}
 
-\Cref{fig:simple} shows a simple fact, although \cref{fig:simple} could also show something else.
+\section{Representing task-oriented supervision}
+\label{sec:repre}
 
-\Cref{tab:simple} shows a simple fact, although \cref{tab:simple} could also show something else.
+\section{Dataset Collection Process}
+\label{sec:collection}
 
-\Cref{sec:intro} shows a simple fact, although \cref{sec:intro} could also show something else.
+\section{Dataset Properties}
+\label{sec:props}
 
-Brackets work as designed:
-<test>
+\section{Related Work}
+\label{sec:related}
 
-The symbol for powerset is now correct: $\powerset$ and not a Weierstrass p ($\wp$).
-
-\begin{inparaenum}
-\item All these items...
-\item ...appear in one line
-\item This is enabled by the paralist package.
-\end{inparaenum}
-
-``something in quotes'' using plain tex or use \enquote{the enquote command}.
-
-\section{Conclusion and Outlook}
+\section{Conclusion and Future work}
+\label{sec:conc}
 
 \subsubsection*{Acknowledgments}
-...
+We would like to thank Ond\v{r}ej Du\v{s}ek for useful comments.
+This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333.
+We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.
+Cloud computational resources were provided by the MetaCentrum under the program LM2010005 and the CERIT-SC under the program Centre CERIT Scientific Cloud, part of the Operational Program Research and Development for Innovations, Reg.\ no.
+CZ.1.05/3.2.00/08.0144.
 
-In the bibliography, use \texttt{\textbackslash textsuperscript} for ``st'', ``nd'', ...:
-E.g., \enquote{The 2\textsuperscript{nd} conference on examples}.
-When you use \href{http://www.jabref.org}{JabRef}, you can use the clean up command to achieve that.
+% ``something in quotes'' using plain tex or use \enquote{the enquote command}.
+% cref Demonstration: Cref at beginning of sentence, cref in all other cases.
+%
+% \Cref{fig:simple} shows a simple fact, although \cref{fig:simple} could also show something else.
+%
+% \Cref{tab:simple} shows a simple fact, although \cref{tab:simple} could also show something else.
+%
+% \Cref{sec:intro} shows a simple fact, although \cref{sec:intro} could also show something else.
+%
+% Brackets work as designed:
+% <test>
+%
+% The symbol for powerset is now correct: $\powerset$ and not a Weierstrass p ($\wp$).
+%
+% \begin{inparaenum}
+% \item All these items...
+% \item ...appear in one line
+% \item This is enabled by the paralist package.
+% \end{inparaenum}
+% In the bibliography, use \texttt{\textbackslash textsuperscript} for ``st'', ``nd'', ...:
+% E.g., \enquote{The 2\textsuperscript{nd} conference on examples}.
+% When you use \href{http://www.jabref.org}{JabRef}, you can use the clean up command to achieve that.
 
+% Winery~\cite{Winery} is graphical \commentontext{modeling}{modeling with one \enquote{l}, because of AE} tool.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-All links were last followed on October 5, 2014.
+All links were last followed on June 28, 2016.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-06-22 paper.tex
table and annotators interface
x

@@
 
-\begin{table}
-\caption{Simple Table}
-
-\label{tab:simple}
-Simple Table
-\end{table}
-
 \section{End-to-end training of dialogue systems}
@@
 
-\section{Representing task-oriented supervision}
+\section{Supervised feedback for task-oriented dialogue}
 \label{sec:repre}
+Traditionally, the dialogue systems are designed as pipelines of components, i.e.\ language understanding (LU) unit, dialogue tracker (DT), dialogue manager (DM) and natural language generator (NLG) for chat-based conversational agents.
+If one want to use speech-to-speech conversational agent the 1-best ASR hypothesis can be used as input for LU unit and the NLG can be easily modified so its output is convenient for text-to-speech (TTS) unit which need to appended to the pipeline.
+
+We focus on preparing training data so the LU, DT, DM and NLG components of dialogue system can be trained using such data.
+The TTS and the ASR modules are typically trained with much more data and such data sets are out of scope of this paper.
+
+It was shown that few hundreds of annotated domain specific conversation is needed for training relatively well performing LU~\cite{Alex} as well as Dialogue State Tracking~\cite{todo-Young?} components.
+The work of~\cite{dusek} and~\cite{Marraise} showed that also several hundreds of conversations with appropriate annotation is needed for training usable NLG unit on simple domains.
+Even the crucial task of action selection with reward provided only at the end of dialogue can be trained using POMDP dialogue manager and few thousands conversations~\cite{Gasic}.
+
+A~novel work of~\cite{Wen} showed that only XY conversation annotated with just at dialogue state level is needed for training the whole end-to-end system performing the task of summarizing the dialogue history and reply planning and generation.
+Consequently, we believe that end-to-end systems even with latent variables can be trained using few hundreds conversation if additional supervision in the form of simple annotation is used for narrow goal-oriented domains such as~\cite{Wen} domain or Cambridge restaurant domain~\cite{DSTC2}.
+
+We note that on one hand further annotation of dialogue conversation may help to train the models faster, but simply collecting more data is typically more beneficial even with less annotation for models which does not require such annotation.
+As a consequence, we see work of~\cite{Wen},~\cite{Borders} and~\cite{Williams} as great step forward since there work use annotation on dialogue state level or even no annotation for training dialogue agents.
+
+On the other hand, we believe that annotating a dialogue state according to expert-handcrafted ontology is both artificial and still very labour intensive data collection task, so our work aim at collecting conversation with lighter but more easier to get annotations.
+We suppose that a task-oriented  domain is defined by a task database e.g.
+in the Cambridge restaurant domain by database containing information about restaurant names, price range, area, address and phone.
+We further suppose that there two roles in the conversation a {\it client} and a {\it operator}.
+Typically, one wants to train a system which replaces the {\it operator} who is the domain expert.
+{\it Clients} seek information stored in the database and use the system instead of human operator to obtain desired information.
+In order to collect cheap high quality training data conversation one can record conversation between human operator and human clients.
+Typically, the operator is provided with interface to the database so it can quickly find relevant information and play the role of domain expert.
+We suggest to collect the operator's database calls with its arguments instead of dialogue state annotation after each turn.
+
+The calls' to the database when call completely represents the client intention which is the purpose of the dialogue state.
+On the other, the database calls are not present in every turn and thus by logging only the calls one loses a possibility to track partially filled client intention.
+We argue that in high quality human-human conversation there is a minimum turns which are related to the domain and do not contain calls to the database as demonstrated in~Section~\ref{sec:props}.
 
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[height=25em]{gui-annotators-client}
+\caption{Annotation interface}
+\end{center}
+\vspace{-0.80em}
+\label{fig:encind}
+\end{figure}
+
 \section{Dataset Properties}
 \label{sec:props}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{lrr}
+\hline
+Set   & \# Dialogues & \# Turns \\
+\hline
+% Joint  &  todo &  todo \\
+% /a/SSD/oplatek/e2end/log/2016-06-08-17-31-38.400-dstc-INDEP_labels-d0.7-w100-e100/
+% /a/SSD/oplatek/e2end/log/TEST-ORIGINAL-2016-06-08-17-31-38.400dstc-INDEP_labels-d0.7-w100-e100-reward-0.9080-step-0036224
+Train  &   ? & ? \\
+Dev &   ? & ? \\
+Test &   ? & ? \\
+\hline
+\end{tabular}
+\caption{Accuracy on development and test set}
+\vspace{-2em}
+\end{center}
+\label{tab:props}
+\end{table}
 

### 2016-06-23 paper.tex
all put loosely together

@@
 
-\begin{figure}
-Simple Figure
-\caption{Simple Figure}
-\label{fig:simple}
-\end{figure}
-
-\section{End-to-end training of dialogue systems}
-\label{sec:training}
+% \section{End-to-end training of dialogue systems}
+% \label{sec:training}
 
@@
 On the other hand, we believe that annotating a dialogue state according to expert-handcrafted ontology is both artificial and still very labour intensive data collection task, so our work aim at collecting conversation with lighter but more easier to get annotations.
-We suppose that a task-oriented  domain is defined by a task database e.g.
-in the Cambridge restaurant domain by database containing information about restaurant names, price range, area, address and phone.
+We suppose that a task-oriented  domain is defined by a task database e.g. in the Cambridge restaurant domain by database containing information about restaurants
 We further suppose that there two roles in the conversation a {\it client} and a {\it operator}.
@@
 
+Our data collection processed aimed at collecting natural conversation in the well defined domain.
+We selected well studied Cambridge restaurant domain since the previous dataset~\cite{dstc1, dstc2, dstc3} in that domain demonstrated that a meaningful and not too long conversation can be held in the domain.
+Also it was proven that the domain is on one hand difficult enough that even the state-of-the art systems does not reach human-level performance in the role of the operator and on the other hand numerous systems~\cite{young, gasic, Wen} demonstrated that are able to provide information to the clients most of the time.
+
+We defined our domain by choosing a database from Dialogue State Tracking Challenge 2 (DSTC2)~\cite{dstc2} and explaining the interlocutors that there two roles a client and a operator.
+For each conversation we determined goals for the client and provided the database for the operator.
+We used the CrowdFlower (CF) crowdsourcing platform to collect the conversations.
+
+We first describe the database which defines our domain in~Section~\ref{sec:db}.
+Then we describe how the hired workers used our interface for playing either client or operator roles in~Sections~\ref{sec:client}and~\ref{sec:operator}.
+Finally, in~Section~\ref{sec:async} we describe how we collected conversations one response at a time without connecting the interlocutors in real-time.
+
+\subsubsection{Domain database}
+\label{sec:db}
+
+We used exactly the same database as provided for the DSTC2 challenge.
+The database contains information about 107 restaurants and their properties stored in the columns:
+
+% \begin{itemize}
+\begin{inparaenum}
+    \item name (107),
+    \item price range (3?),
+    \item area (4),
+    \item food (20?),
+    \item address (90?),
+    \item phone (90?),
+    \item postcode (90?).
+\end{inparaenum}
+% \end{itemize}
+
+We include the size of the vocabulary in brackets for each column.
+The address or the postcode are unique for each restaurant but are sometimes missing, but the name of the restaurant is always known. 
+There typically multiple restaurant with the same price range, area, or food type property.
+These properties are sometimes unknown as well.
+
+We use the database to generate the clients goals as demonstrated in~Figure~\ref{fig:client}, but only the operator is able to search the database (see~Figure~\ref{fig:operator}).
+
+\subsubsection{Client interface}
+\label{sec:client}
+
+The client is given a goal to request provided information from the operator.
+He may choose not to seek the goal immediately but submit more appropriate response such as greeting first.
+The goals for the client are presented to the CF workers gradually and may contradict each other.
+For example, the client may at first want a Chinese food, but later it changes her mind and wants to find restaurant serving British food.
+
+Before submitting a reply the client is instructed to read the dialogue history and marked the goals which were presented to the operator.
+The worker in the role of client is paid for each submitted response.
+
 \begin{figure}
@@
 \includegraphics[height=25em]{gui-annotators-client}
-\caption{Annotation interface}
+\caption{Client annotation interface}
 \end{center}
 \vspace{-0.80em}
-\label{fig:encind}
+\label{fig:client}
 \end{figure}
+
+\subsubsection{Operator database}
+\label{sec:operator}
+The operator is asked to politely reply the clients needs according the information stored in the database.
+In order to provide the informations to clients the operator uses the DB interface depicted in~Figure~\ref{fig:operator}.
+Her or she filters the restaurants using a full text search on the database.
+The content of the database is intentional hidden if no filter is specified so the filter has to be used.
+The CF workers are also instructed also explicitly mark the rows of the restaurants about which provide the information in their answer.
+
+\begin{figure}
+\begin{center}
+\includegraphics[height=25em]{gui-annotators-system}
+\caption{Operator annotation interface}
+\end{center}
+\vspace{-0.80em}
+\label{fig:operator}
+\end{figure}
+
+\subsubsection{Asynchronous collection without real-time responses}
+\label{sec:async}
+We design the crowdsourcing jobs so the CF contributors are able to work independently to each other.
+One conversation is collected through out several rounds of jobs.
+The roles of client and operator take turns as sets of partial conversations are submitted for collecting a single new response.
+As a consequence, multiple contributors participate in submitting responses for single conversation for both roles.
+
+Each utterance in conversation is submitted by different contributor, so contributors need to read carefully the dialogue history to understand the conversation before submitting their response.
+The workers are able to mark dialogues which does not make sense and thus they self-assess quality of the conversations.
+Note also that the conversation are typically rather short taking only from {\bf TODO} four to six turns including first turn with greetings.
+The contributors mark the conversations as finished if they have no more goals to fulfill and all the goodbyes were said.
+
+We bootstrap the conversation with either with an operators introduction "{\it Hello , welcome to the Cambridge restaurant system?
+You can ask for restaurants by area , price range or food type .
+How may I help you?}" and the first contributors play role of the client or we bootstrap the conversation full turn with aforementioned operators utterance and clients greeting e.g.
+"Hi" so the contributors play role of the operator.
+
+To avoid poor language level of English we restricted the CF worker to English-speaking countries.
+We further perform heuristically check for too trivial answers and we added ability to the CF workers to rate each others submission.
+It help us filter low quality submission, but more importantly it motivated workers not to cheat.
+
+% TODO describe how we started with 5 bootstrapped conversation with client role 5 without it and then mixed the partial with new one and resubmit them until the first conversations were marked as finished.
 
@@
 \label{sec:props}
+
+We collected XY conversation with average length ZY.
+During an average conversation 2.4-TODO tasks are requested and answered.
+Typically in 65-TODO \% case the conversation is ended by the client
 
@@
 
+During the data collection process we discarded roughly 40-TODO \% of conversation in total.
+
 \section{Related Work}
@@
 
+Our work is closely related  to work of~\cite{dstc1, dstc2, dstc3} in the sense that the conversation are held in the same domain.
+On the other hand, the collection process differs substantially because we do not use any artificial system and rather we focus on collecting high quality human conversations.
+In addition, in our work we do not collect complicated annotation on LU and DST level as it was previously done on DST challenges.
+
+A very relevant work of~\cite{Wen} collected human-human dialogues in similar domain to the Cambridge domain according their description.
+Their dataset is not yet published so we compare only with their statistics.
+The dataset is of similar size and used very similar collection scheme where the Amazon Mechanical Turk workers submitted one reply at a time without being connected to each other in real-time.
+
+Another line of research~\cite{mirek-interactive} used CF to collect human-human conversation for interactive-learning dataset.
+However, the collected dialogues were later annotated by expert annotators which goes directly against our intentions to avoid any expensive annotations.
+
+There is tremendous amount of work describing Wizard of Oz experiments~\cite{walker,schlangen,someone} which either focused on studying linguistic properties of dialogues, evaluated proof of concept or even collected bootstrap training data, but definitely, according our knowledge, do not use cheap crowdsourcing workers to collect a~full training dataset.
+
 \section{Conclusion and Future work}
 \label{sec:conc}
+We present a new human-human dialogue dataset with annotation of user intension in form of their database calls.
+We also introduced a novel data collection setting which resembles work of operators in call centers and introduce minimum overhead to crowdsourcing workers.
+
+The collected dialogues are published under Creative Commons 4.0 BY-SA license on available to download at {\it anonymised}.  % lindat\footnote{todo where}.
 

### 2016-06-24 paper.tex
x
citations

@@
 
-\title{Collecting operator-client conversation aligned with knowledge-base queries}
+\title{Dataset of operator-client dialogues aligned with knowledge-base queries}
 %If Title is too long, use \titlerunning
@@
 
-Current Spoken Dialogue Systems (SDS) are either handcrafted and use no training data\cite{alex},\cite{todo}, but require non-trivial amount of expert work, or are gradually improved from initial policy through live user interaction\cite{Pomdp-young,gasix}, and lately are trained using supervised learning typically in end-to-end manner\cite{Wen2016,Williams2016}.\footnote{The~work of \cite{Williams2016} also fine tuned the conversation with reinforcement learning after the supervised-learning stage.}
-The reinforce learning on one hand need just collect enough live user conversation without any transcription with the exception of explicit feedback at the end of each dialogue, but because the feedback signal is typically rather noise and delayed one require thousands of live conversations to improve rather simple policy.\cite{gasic}
-The supervised-learning methods greatly reduced the number of conversation needed for training reasonable policy to few hundreds\cite{Wen2016}, but require annotation for all components used the dialogue which so far included at least a dialogue state\cite{Wen, his}.
+Current Spoken Dialogue Systems (SDS) are either handcrafted and use no training data\cite{duvsek2014alex},\cite{raux2005let}, but require non-trivial amount of expert work, or are gradually improved from initial policy through live user interaction\cite{young2010hidden,gasic2011line}, and lately are trained using supervised learning typically in end-to-end manner\cite{wen2016network,williams2016end}.\footnote{The~work of \cite{williams2016end} also fine tuned the conversation with reinforcement learning after the supervised-learning stage.}
+The reinforce learning on one hand need just collect enough live user conversation without any transcription with the exception of explicit feedback at the end of each dialogue, but because the feedback signal is typically rather noise and delayed one require thousands of live conversations to improve rather simple policy.\cite{gasic2011line}
+The supervised-learning methods greatly reduced the number of conversation needed for training reasonable policy to few hundreds\cite{wen2016network}, but require annotation for all components used the dialogue which so far included at least a dialogue state\cite{wen2016network, young2010hidden}.
 Since the dialogue state is simplification of dialogue history and has no broadly-accepted form, it is very expensive to collect such annotated data because the dialogue state typically differs among domains and its structure is hard to explain to annotators.
-In this paper, we focus on collecting supervised training set with rich enough annotation so the supervised models similar to~\cite{Wen2016} can be trained with few hundreds of dialogues, but the annotation of dialogues are much easier to collect.
+In this paper, we focus on collecting supervised training set with rich enough annotation so the supervised models similar to~\cite{wen2016network} can be trained with few hundreds of dialogues, but the annotation of dialogues are much easier to collect.
 
 We believe that the present dataset can be used for first experiments for end-to-end systems using supervised learning without annotated dialogue state.
-The resulting systems should be able to roughly compare to systems trained on datasets with \cite{dstsc2, dstc3} dialogue state annotation because the same settings, i.e.\ database and task, for data collection.
+The resulting systems should be able to roughly compare to systems trained on datasets with \cite{williams2013dstc1, henderson2014dstc2, henderson2014dstc3} dialogue state annotation because the same settings, i.e.\ database and task, for data collection.
 Despite the fact, we collected human-to-human dialogues on known task of Cambridge restaurant domains the data-collecting method is completely domain and language independent.
@@
 
-It was shown that few hundreds of annotated domain specific conversation is needed for training relatively well performing LU~\cite{Alex} as well as Dialogue State Tracking~\cite{todo-Young?} components.
-The work of~\cite{dusek} and~\cite{Marraise} showed that also several hundreds of conversations with appropriate annotation is needed for training usable NLG unit on simple domains.
-Even the crucial task of action selection with reward provided only at the end of dialogue can be trained using POMDP dialogue manager and few thousands conversations~\cite{Gasic}.
+It was shown that few hundreds of annotated domain specific conversation is needed for training relatively well performing LU~\cite{duvsek2014alex} as well as Dialogue State Tracking~\cite{young2010hidden} components.
+The work of~\cite{duvsek2014alex} and~\cite{mairesse2010phrase} showed that also several hundreds of conversations with appropriate annotation is needed for training usable NLG unit on simple domains.
+Even the crucial task of action selection with reward provided only at the end of dialogue can be trained using POMDP dialogue manager and few thousands conversations~\cite{gasic2011line}.
 
-A~novel work of~\cite{Wen} showed that only XY conversation annotated with just at dialogue state level is needed for training the whole end-to-end system performing the task of summarizing the dialogue history and reply planning and generation.
-Consequently, we believe that end-to-end systems even with latent variables can be trained using few hundreds conversation if additional supervision in the form of simple annotation is used for narrow goal-oriented domains such as~\cite{Wen} domain or Cambridge restaurant domain~\cite{DSTC2}.
+A~novel work of~\cite{wen2016network} showed that only XY conversation annotated with just at dialogue state level is needed for training the whole end-to-end system performing the task of summarizing the dialogue history and reply planning and generation.
+Consequently, we believe that end-to-end systems even with latent variables can be trained using few hundreds conversation if additional supervision in the form of simple annotation is used for narrow goal-oriented domains such as~\cite{wen2016network} domain or Cambridge restaurant domain~\cite{henderson2014dstc2}.
 
 We note that on one hand further annotation of dialogue conversation may help to train the models faster, but simply collecting more data is typically more beneficial even with less annotation for models which does not require such annotation.
-As a consequence, we see work of~\cite{Wen},~\cite{Borders} and~\cite{Williams} as great step forward since there work use annotation on dialogue state level or even no annotation for training dialogue agents.
+As a consequence, we see work of~\cite{wen2016network},~\cite{bordes2016learning} and~\cite{williams2016end} as great step forward since there work use annotation on dialogue state level or even no annotation for training dialogue agents.
 
@@
 Our data collection processed aimed at collecting natural conversation in the well defined domain.
-We selected well studied Cambridge restaurant domain since the previous dataset~\cite{dstc1, dstc2, dstc3} in that domain demonstrated that a meaningful and not too long conversation can be held in the domain.
-Also it was proven that the domain is on one hand difficult enough that even the state-of-the art systems does not reach human-level performance in the role of the operator and on the other hand numerous systems~\cite{young, gasic, Wen} demonstrated that are able to provide information to the clients most of the time.
+We selected well studied Cambridge restaurant domain since the previous dataset~\cite{williams2013dstc1, henderson2014dstc2, henderson2014dstc3} in that domain demonstrated that a meaningful and not too long conversation can be held in the domain.
+Also it was proven that the domain is on one hand difficult enough that even the state-of-the art systems does not reach human-level performance in the role of the operator and on the other hand numerous systems~\cite{young2010hidden, gasic2011line, wen2016network} demonstrated that are able to provide information to the clients reasonable well.
 
-We defined our domain by choosing a database from Dialogue State Tracking Challenge 2 (DSTC2)~\cite{dstc2} and explaining the interlocutors that there two roles a client and a operator.
+We defined our domain by choosing a database from Dialogue State Tracking Challenge 2 (DSTC2)~\cite{henderson2014dstc2} and explaining the interlocutors that there two roles a client and a operator.
 For each conversation we determined goals for the client and provided the database for the operator.
@@
 
-Our work is closely related  to work of~\cite{dstc1, dstc2, dstc3} in the sense that the conversation are held in the same domain.
+Our work is closely related  to work of~\cite{williams2013dstc1, henderson2014dstc2, henderson2014dstc3} in the sense that the conversation are held in the same domain.
 On the other hand, the collection process differs substantially because we do not use any artificial system and rather we focus on collecting high quality human conversations.
@@
 
-A very relevant work of~\cite{Wen} collected human-human dialogues in similar domain to the Cambridge domain according their description.
+A very relevant work of~\cite{wen2016network} collected human-human dialogues in similar domain to the Cambridge domain according their description.
 Their dataset is not yet published so we compare only with their statistics.
@@
 
-Another line of research~\cite{mirek-interactive} used CF to collect human-human conversation for interactive-learning dataset.
+Another line of research~\cite{vodolan2016data} used CF to collect human-human conversation for interactive-learning dataset.
 However, the collected dialogues were later annotated by expert annotators which goes directly against our intentions to avoid any expensive annotations.
 
-There is tremendous amount of work describing Wizard of Oz experiments~\cite{walker,schlangen,someone} which either focused on studying linguistic properties of dialogues, evaluated proof of concept or even collected bootstrap training data, but definitely, according our knowledge, do not use cheap crowdsourcing workers to collect a~full training dataset.
+There is significant amount of work which used Wizard of Oz experiments~\cite{whittaker2002fish,walker1997evaluating,rieser2008learning} for studying linguistic properties of dialogues, evaluating proof of concept or even collecting bootstrap training data, but according our knowledge no other work than~\cite{We} have not used cheap crowdsourcing workers to collect a~full training dataset for supervised learning.
 
@@
 We also introduced a novel data collection setting which resembles work of operators in call centers and introduce minimum overhead to crowdsourcing workers.
+The collected dialogues are published under Creative Commons 4.0 BY-SA license on available to download at {\it anonymised}.  % lindat\footnote{todo where}.
 
-The collected dialogues are published under Creative Commons 4.0 BY-SA license on available to download at {\it anonymised}.  % lindat\footnote{todo where}.
+We plan to increase the number of collected dialogues till the camera ready deadline to XYZU.
+We intend to use the dataset to train and evaluate an~end-to-end conversational model which uses only the database calls as additional supervision to the recorded responses.
 

### 2016-06-24 paper.tex
latest comments

@@
 \begin{abstract}
-    This paper presents a novel datasets for training end-to-end task oriented conversational agents.
-    The dataset contains task oriented conversation between an operator, a task expert, and a client who is seeking information about the task along with records of data base API calls of the operator, which capture the distilled meaning of the user query.
+    This paper presents a novel dataset for training end-to-end task oriented conversational agents.
+    The dataset contains task oriented conversations between an operator, a task expert, and a client who is seeking information about the task along with records of data base API calls of the operator, which capture the distilled meaning of the user query.
     The data base calls represent not only instantiation of user wishes but also, when evaluated against the database determine the answer from the database, which were used by the operator to provide requested information to the client.
@@
 
-Current Spoken Dialogue Systems (SDS) are either handcrafted and use no training data\cite{duvsek2014alex},\cite{raux2005let}, but require non-trivial amount of expert work, or are gradually improved from initial policy through live user interaction\cite{young2010hidden,gasic2011line}, and lately are trained using supervised learning typically in end-to-end manner\cite{wen2016network,williams2016end}.\footnote{The~work of \cite{williams2016end} also fine tuned the conversation with reinforcement learning after the supervised-learning stage.}
+Current Spoken Dialogue Systems (SDS) are either handcrafted and use no training data\cite{duvsek2014alex,raux2005let}, but require non-trivial amount of expert work, or are gradually improved from initial policy through live user interaction\cite{young2010hidden,gasic2011line}, and lately are trained using supervised learning typically in end-to-end manner\cite{wen2016network,williams2016end}.\footnote{The~work of \cite{williams2016end} also fine tuned the conversation with reinforcement learning after the supervised-learning stage.}
 The reinforce learning on one hand need just collect enough live user conversation without any transcription with the exception of explicit feedback at the end of each dialogue, but because the feedback signal is typically rather noise and delayed one require thousands of live conversations to improve rather simple policy.\cite{gasic2011line}
-The supervised-learning methods greatly reduced the number of conversation needed for training reasonable policy to few hundreds\cite{wen2016network}, but require annotation for all components used the dialogue which so far included at least a dialogue state\cite{wen2016network, young2010hidden}.
+The supervised-learning methods greatly reduced the number of conversation needed for training reasonable policy to few hundreds\cite{wen2016network}, but require annotation for all components used the dialogue which so far included at least a dialogue state\cite{wen2016network,young2010hidden}.
 Since the dialogue state is simplification of dialogue history and has no broadly-accepted form, it is very expensive to collect such annotated data because the dialogue state typically differs among domains and its structure is hard to explain to annotators.
@@
 We believe that the present dataset can be used for first experiments for end-to-end systems using supervised learning without annotated dialogue state.
-The resulting systems should be able to roughly compare to systems trained on datasets with \cite{williams2013dstc1, henderson2014dstc2, henderson2014dstc3} dialogue state annotation because the same settings, i.e.\ database and task, for data collection.
+The resulting systems should be able to roughly compare to systems trained on datasets with~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3} dialogue state annotation because the same settings, i.e.\ database and task, for data collection.
 Despite the fact, we collected human-to-human dialogues on known task of Cambridge restaurant domains the data-collecting method is completely domain and language independent.
@@
 
-We note that on one hand further annotation of dialogue conversation may help to train the models faster, but simply collecting more data is typically more beneficial even with less annotation for models which does not require such annotation.
-As a consequence, we see work of~\cite{wen2016network},~\cite{bordes2016learning} and~\cite{williams2016end} as great step forward since there work use annotation on dialogue state level or even no annotation for training dialogue agents.
+We note that further annotation of dialogue conversation may help to train the models faster, but simply collecting more data is typically more beneficial.
+As a consequence, we see works~\cite{wen2016network,bordes2016learning,williams2016end} as important step forward since there work use annotation only on dialogue state level or even no annotation at all for training dialogue agents.
 
-On the other hand, we believe that annotating a dialogue state according to expert-handcrafted ontology is both artificial and still very labour intensive data collection task, so our work aim at collecting conversation with lighter but more easier to get annotations.
-We suppose that a task-oriented  domain is defined by a task database e.g. in the Cambridge restaurant domain by database containing information about restaurants
+On the other hand, we believe that annotating a dialogue state according to expert-handcrafted ontology is both artificial and still very labor-intensive data collection task, so our work aim at collecting conversation with lighter but more easier to get annotations.
+We suppose that a task-oriented  domain is defined by a task database e.g. in the Cambridge restaurant domain by database containing information about restaurants. 
 We further suppose that there two roles in the conversation a {\it client} and a {\it operator}.
@@
 Our data collection processed aimed at collecting natural conversation in the well defined domain.
-We selected well studied Cambridge restaurant domain since the previous dataset~\cite{williams2013dstc1, henderson2014dstc2, henderson2014dstc3} in that domain demonstrated that a meaningful and not too long conversation can be held in the domain.
-Also it was proven that the domain is on one hand difficult enough that even the state-of-the art systems does not reach human-level performance in the role of the operator and on the other hand numerous systems~\cite{young2010hidden, gasic2011line, wen2016network} demonstrated that are able to provide information to the clients reasonable well.
+We selected well studied Cambridge restaurant domain since the previous dataset~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3} in that domain demonstrated that a meaningful and not too long conversation can be held in the domain.
+Also it was proven that the domain is on one hand difficult enough that even the state-of-the art systems does not reach human-level performance in the role of the operator and on the other hand numerous systems~\cite{young2010hidden,gasic2011line,wen2016network} demonstrated that are able to provide information to the clients reasonable well.
 
@@
 We used exactly the same database as provided for the DSTC2 challenge.
-The database contains information about 107 restaurants and their properties stored in the columns:
-
+The database contains information about 107 restaurants and their properties stored in the columns.
+We include the size of the vocabulary in brackets for each column:
 % \begin{itemize}
@@
 
-We include the size of the vocabulary in brackets for each column.
 The address or the postcode are unique for each restaurant but are sometimes missing, but the name of the restaurant is always known. 
-There typically multiple restaurant with the same price range, area, or food type property.
-These properties are sometimes unknown as well.
+There are typically multiple restaurant with the same price range, area, or food type property and these properties might be unknown for a restaurant.
 
-We use the database to generate the clients goals as demonstrated in~Figure~\ref{fig:client}, but only the operator is able to search the database (see~Figure~\ref{fig:operator}).
+Note that we use the database to generate the clients goals as demonstrated in~Figure~\ref{fig:client} and only the operator is able to search the database add demonstrated in~Figure~\ref{fig:operator}.
 
@@
 Before submitting a reply the client is instructed to read the dialogue history and marked the goals which were presented to the operator.
-The worker in the role of client is paid for each submitted response.
 
@@
 The operator is asked to politely reply the clients needs according the information stored in the database.
-In order to provide the informations to clients the operator uses the DB interface depicted in~Figure~\ref{fig:operator}.
+In order to provide the information to clients the operator uses the DB interface depicted in~Figure~\ref{fig:operator}.
 Her or she filters the restaurants using a full text search on the database.
@@
 It help us filter low quality submission, but more importantly it motivated workers not to cheat.
+
+The workers are paid for every submitted response the same amount independently if they play client or operator role.
+The roles are assigned independently.
 
@@
 On the other hand, the collection process differs substantially because we do not use any artificial system and rather we focus on collecting high quality human conversations.
-In addition, in our work we do not collect complicated annotation on LU and DST level as it was previously done on DST challenges.
+In addition, in our work we do not collect complicated annotations on LU and DST level.
 
-A very relevant work of~\cite{wen2016network} collected human-human dialogues in similar domain to the Cambridge domain according their description.
+A~relevant work of~\cite{wen2016network} collected human-human dialogues in similar domain to the Cambridge domain according their description.
 Their dataset is not yet published so we compare only with their statistics.
@@
 \label{sec:conc}
-We present a new human-human dialogue dataset with annotation of user intension in form of their database calls.
+We present a new human-human dialogue dataset with annotation of user intention in form of their database calls.
 We also introduced a novel data collection setting which resembles work of operators in call centers and introduce minimum overhead to crowdsourcing workers.
-The collected dialogues are published under Creative Commons 4.0 BY-SA license on available to download at {\it anonymised}.  % lindat\footnote{todo where}.
+The collected dialogues are published under Creative Commons 4.0 BY-SA license on available to download at {\it anonymized}.  % lindat\footnote{todo where}.
 
@@
 We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.
-Cloud computational resources were provided by the MetaCentrum under the program LM2010005 and the CERIT-SC under the program Centre CERIT Scientific Cloud, part of the Operational Program Research and Development for Innovations, Reg.\ no.
+Cloud computational resources were provided by the MetaCentrum under the program LM2010005 and the CERIT-SC under the program Center CERIT Scientific Cloud, part of the Operational Program Research and Development for Innovations, Reg.\ no.
 CZ.1.05/3.2.00/08.0144.

### 2016-06-24 paper.tex
Update on Overleaf.

@@
     The data base calls represent not only instantiation of user wishes but also, when evaluated against the database determine the answer from the database, which were used by the operator to provide requested information to the client.
-    We expect that this additional supervision of recording database interaction will provide enough information so the task of the conversation can be understood and behaviour of the interlocutors reconstructed by software agents.
-    The dataset was collected using crowdsourcing in offline setting, where each contributor played role either of an operator or a client and contributed single utterance.
+    We expect that this additional supervision of recording database interaction will provide enough information so the task of the conversation can be understood and behavior of the interlocutors reconstructed by software agents.
+    The dataset was collected using crowd-sourcing in offline setting, where each contributor played role either of an operator or a client and contributed single utterance.
     The quality of the data were enforced by mutual control among contributors and manually verified on random sub-sample.
@@
 
-On the other hand, we believe that annotating a dialogue state according to expert-handcrafted ontology is both artificial and still very labor-intensive data collection task, so our work aim at collecting conversation with lighter but more easier to get annotations.
-We suppose that a task-oriented  domain is defined by a task database e.g. in the Cambridge restaurant domain by database containing information about restaurants. 
+We believe that annotating a dialogue state according to expert-handcrafted ontology is both an~artificial and a~very labor-intensive data collection task, so our work aim at collecting conversation with lighter but more easier to get annotations.
+We suppose that a task-oriented  domain is defined by a task database\footnote{In the Cambridge restaurant domain the database is a simple table containing information about restaurants.}. 
 We further suppose that there two roles in the conversation a {\it client} and a {\it operator}.
@@
 {\it Clients} seek information stored in the database and use the system instead of human operator to obtain desired information.
-In order to collect cheap high quality training data conversation one can record conversation between human operator and human clients.
-Typically, the operator is provided with interface to the database so it can quickly find relevant information and play the role of domain expert.
+We suggest to record conversation between human operator and human clients through crowd-sourcing and by this means collect cheap high quality training data.
+Similar recording setup is known from call centers where the operator is provided with interface to the database so it quickly finds relevant information and plays the role of domain expert.
 We suggest to collect the operator's database calls with its arguments instead of dialogue state annotation after each turn.
@@
 Our data collection processed aimed at collecting natural conversation in the well defined domain.
-We selected well studied Cambridge restaurant domain since the previous dataset~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3} in that domain demonstrated that a meaningful and not too long conversation can be held in the domain.
+We decided to collect new dataset int the~well studied Cambridge restaurant domain since the previous datasets~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3} in that domain demonstrated that a meaningful and not too long conversation can be held in the domain.
 Also it was proven that the domain is on one hand difficult enough that even the state-of-the art systems does not reach human-level performance in the role of the operator and on the other hand numerous systems~\cite{young2010hidden,gasic2011line,wen2016network} demonstrated that are able to provide information to the clients reasonable well.
@@
 For each conversation we determined goals for the client and provided the database for the operator.
-We used the CrowdFlower (CF) crowdsourcing platform to collect the conversations.
+We used the CrowdFlower (CF) crowd-sourcing platform for collecting the conversations.
 
 We first describe the database which defines our domain in~Section~\ref{sec:db}.
-Then we describe how the hired workers used our interface for playing either client or operator roles in~Sections~\ref{sec:client}and~\ref{sec:operator}.
+Then we describe how the hired workers used our interface for playing either client or operator roles in~Sections~\ref{sec:client} and~\ref{sec:operator}.
 Finally, in~Section~\ref{sec:async} we describe how we collected conversations one response at a time without connecting the interlocutors in real-time.
@@
 \label{sec:async}
-We design the crowdsourcing jobs so the CF contributors are able to work independently to each other.
+We design the crowd-sourcing jobs so the CF contributors are able to work independently to each other.
 One conversation is collected through out several rounds of jobs.
@@
 The workers are able to mark dialogues which does not make sense and thus they self-assess quality of the conversations.
-Note also that the conversation are typically rather short taking only from {\bf TODO} four to six turns including first turn with greetings.
+Note also that the conversation are typically rather short.
 The contributors mark the conversations as finished if they have no more goals to fulfill and all the goodbyes were said.
 
-We bootstrap the conversation with either with an operators introduction "{\it Hello , welcome to the Cambridge restaurant system?
+We bootstrap the conversation either with an operators introduction "{\it Hello , welcome to the Cambridge restaurant system?
 You can ask for restaurants by area , price range or food type .
-How may I help you?}" and the first contributors play role of the client or we bootstrap the conversation full turn with aforementioned operators utterance and clients greeting e.g.
-"Hi" so the contributors play role of the operator.
+How may I help you?}" or we bootstrap the conversation with a~full turn where we add clients greeting e.g.
+{\it "Hi"} to aforementioned operators utterance.
+If we initialize the dialogue with a~full turn the first contributor plays role of the system if we bootstrap the conversation only with~the operators greeting, the contributors plays the client's role.
 
@@
 We further perform heuristically check for too trivial answers and we added ability to the CF workers to rate each others submission.
-It help us filter low quality submission, but more importantly it motivated workers not to cheat.
+It help us filter low quality conversations, but more importantly it motivated workers not to cheat.
 
 The workers are paid for every submitted response the same amount independently if they play client or operator role.
-The roles are assigned independently.
+The roles are assigned randomly.
 
@@
 Typically in 65-TODO \% case the conversation is ended by the client
-
+As we mention the conversation are short, taking only from {\bf TODO} four to six turns including first turn with greetings.
 \begin{table}
@@
 During the data collection process we discarded roughly 40-TODO \% of conversation in total.
+We split the XYZ collected conversation randomly into training, development and test set (see Table~\ref{tab:props}).
 
@@
 
-Our work is closely related  to work of~\cite{williams2013dstc1, henderson2014dstc2, henderson2014dstc3} in the sense that the conversation are held in the same domain.
+Our work is closely related  to work of~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3} in the sense that the conversation are held in the same domain.
 On the other hand, the collection process differs substantially because we do not use any artificial system and rather we focus on collecting high quality human conversations.
@@
 
-There is significant amount of work which used Wizard of Oz experiments~\cite{whittaker2002fish,walker1997evaluating,rieser2008learning} for studying linguistic properties of dialogues, evaluating proof of concept or even collecting bootstrap training data, but according our knowledge no other work than~\cite{We} have not used cheap crowdsourcing workers to collect a~full training dataset for supervised learning.
+There is significant amount of work which used Wizard of Oz experiments~\cite{whittaker2002fish,walker1997evaluating,rieser2008learning} for studying linguistic properties of dialogues, evaluating proof of concept or even collecting bootstrap training data, but according our knowledge no other work than~\cite{wen2016network} have not used cheap crowd-sourcing workers to collect a~full training dataset for supervised learning.
 
@@
 We present a new human-human dialogue dataset with annotation of user intention in form of their database calls.
-We also introduced a novel data collection setting which resembles work of operators in call centers and introduce minimum overhead to crowdsourcing workers.
+We also introduced a novel data collection setting which resembles work of operators in call centers and introduce minimum overhead to crowd-sourcing workers.
 The collected dialogues are published under Creative Commons 4.0 BY-SA license on available to download at {\it anonymized}.  % lindat\footnote{todo where}.

### 2016-06-24 paper.tex
Update on Overleaf.

@@
 % \iffalse % FIXME enable for blind review and ucomment Single institute with filled values
+
 \iftrue % FIXME enable for blind review and ucomment Single institute with filled values 
-%Multiple institutes are typeset as follows:
-\author{Firstname Lastname\inst{1} \and Firstname Lastname\inst{2} }
-%If there are too many authors, use \authorrunning
-%\authorrunning{First Author et al.}
-
+\author{Firstname Lastname \and Firstname Lastname }
 \institute{
-Insitute 1\\
-\email{...}\and
-Insitute 2\\
-\email{...}
+Insitute\\
+\email{anonym@anonymous}
 }
@@
 
-The paper is structured as follows:
-XY
+The paper is structured as follows: The~Section~\ref{sec:repre} motivates the annotations and format of our dataset.
+In the Section~\ref{sec:collection} we introduce our collection process using crowd-sourcing.
+Section~\ref{sec:props} presents the dataset properties and we list the related work in the~Section~\ref{sec:related}.
+We conclude the paper and suggest future work in~Section~\ref{sec:conc}.
 
@@
 
-\subsubsection{Domain database}
+\subsection{Domain database}
 \label{sec:db}
@@
 
-\subsubsection{Client interface}
+\subsection{Client interface}
 \label{sec:client}
@@
 
-\subsubsection{Operator database}
+\subsection{Operator interface}
 \label{sec:operator}
@@
 
-\subsubsection{Asynchronous collection without real-time responses}
+\subsection{Asynchronous collection without real-time responses}
 \label{sec:async}
 We design the crowd-sourcing jobs so the CF contributors are able to work independently to each other.
-One conversation is collected through out several rounds of jobs.
 The roles of client and operator take turns as sets of partial conversations are submitted for collecting a single new response.
@@
 The workers are able to mark dialogues which does not make sense and thus they self-assess quality of the conversations.
-Note also that the conversation are typically rather short.
 The contributors mark the conversations as finished if they have no more goals to fulfill and all the goodbyes were said.
@@
 
+In single job submission we let the workers append to each dialogue a~single response.
+Typically, we submit from twenty to thirty partial dialogues with different history lengths.
+Some conversations might be just initialized with the auto-generated greetings but most of them store multiple turns collected by CF contributors in the~previous submission.
+Note also that the conversations are typically rather short so full dialogues are collected after few rounds of submissions.
+The workers are paid for every submitted response the same amount independently if they play client or operator role and they typically contribute to multiple conversation during one job submission.
+The contributors are assigned roles randomly.
+
 To avoid poor language level of English we restricted the CF worker to English-speaking countries.
@@
 It help us filter low quality conversations, but more importantly it motivated workers not to cheat.
-
-The workers are paid for every submitted response the same amount independently if they play client or operator role.
-The roles are assigned randomly.
 
@@
 This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333.
-We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.
-Cloud computational resources were provided by the MetaCentrum under the program LM2010005 and the CERIT-SC under the program Center CERIT Scientific Cloud, part of the Operational Program Research and Development for Innovations, Reg.\ no.
+% We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.
+% Cloud computational resources were provided by the MetaCentrum under the program LM2010005 and the CERIT-SC under the program Center CERIT Scientific Cloud, part of the Operational Program Research and Development for Innovations, Reg.\ no.
 CZ.1.05/3.2.00/08.0144.

### 2016-06-27 paper.tex
Update on Overleaf.

@@
 \usepackage[english]{babel}
+\usepackage[utf8]{inputenc}
 
@@
 
+\usepackage[normalem]{ulem}
+
+\def\OP#1{{\color{red}OP: \it #1}}
+\def\ODdel#1{\bgroup\markoverwith{\textcolor{red}{\rule[0.5ex]{2pt}{1pt}}}\ULon{#1}}
+
+\definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}
+\def\OD#1{{\color{darkgreen}OD: \it #1}}
+\def\ODdel#1{\bgroup\markoverwith{\textcolor{darkgreen}{\rule[0.5ex]{2pt}{1pt}}}\ULon{#1}}
+%\def\OD#1{\relax} % make my comments vanish
+%\def\ODdel#1{#1} % make my comments vanish
+
 \begin{document}
@@
 \title{Dataset of operator-client dialogues aligned with knowledge-base queries}
-%If Title is too long, use \titlerunning
-%\titlerunning{Short Title}
 
-% %Single insitute
-% \author{Ond\v{r}ej Pl\'{a}tek \and Filip Jur\v{c}\'{i}\v{c}ek}
-% %If there are too many authors, use \authorrunning
-% %\authorrunning{First Author et al.}
-% \institute{Charles University in Prague, Faculty of Mathematics and Physics \\
-% Insitute of Formal and Applied Linguistics \\
-% Malostransk\'{e} n\'{a}m\v{e}st\'i 25, 11800 Praha 1, Czech Republic \\
-% \email{\{oplatek,jurcicek\}@ufal.mff.cuni.cz}}
+\author{Ondřej Plátek \and Filip Jurčíček}
+\institute{Charles University in Prague, Faculty of Mathematics and Physics \\
+Institute of Formal and Applied Linguistics \\
+Malostranské náměstí 25, 11800 Praha 1, Czech Republic \\
+\email{\{oplatek,jurcicek\}@ufal.mff.cuni.cz}}
 
-%Multiple insitutes
-%Currently disabled
-%
-% \iffalse % FIXME enable for blind review and ucomment Single institute with filled values
-
-\iftrue % FIXME enable for blind review and ucomment Single institute with filled values 
+\iftrue % FIXME uncomment for final submission
 \author{Firstname Lastname \and Firstname Lastname }
@@
 
+\OP{Fill missing values about the dataset collected so far} \\
+\OP{describe the dataset,apologize for not having the dataset collected - promise for camera ready version.} \\
+\OP{grammar check} \\
+
 \begin{abstract}
     This paper presents a novel dataset for training end-to-end task oriented conversational agents.
-    The dataset contains task oriented conversations between an operator, a task expert, and a client who is seeking information about the task along with records of data base API calls of the operator, which capture the distilled meaning of the user query.
-    The data base calls represent not only instantiation of user wishes but also, when evaluated against the database determine the answer from the database, which were used by the operator to provide requested information to the client.
-    We expect that this additional supervision of recording database interaction will provide enough information so the task of the conversation can be understood and behavior of the interlocutors reconstructed by software agents.
-    The dataset was collected using crowd-sourcing in offline setting, where each contributor played role either of an operator or a client and contributed single utterance.
-    The quality of the data were enforced by mutual control among contributors and manually verified on random sub-sample.
+    The dataset contains task oriented conversations between an operator – a task expert, and a client who is seeking information about the task, along with records of database API calls performed by the operator, which capture the distilled meaning of the user query.
+    We expect that thanks to this easy-to-get supervision of database calls one would require significantly less training data for training end-to-end dialogue agents.
+ 	The dataset is collected using crowdsourcing on well known restaurant domain.
+    The quality of the data is enforced by mutual control among contributors and manually verified on random sub-sample.
     The dataset is available for download under the Creative Commons 4.0 BY-SA license.
@@
 \section{Introduction}\label{sec:intro}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We present a new dataset of human-human task-oriented conversation in domain of Cambridge restaurant services targeted for supervised training of autonomous systems to play role of the operator which provides information about the restaurants to clients.
-In contrast to previously released datasets, our datasets contains easy to obtain high-quality transcriptions of the client and operator actions during conversations.
-We introduce a~very little overhead by collecting data base calls in addition to the transcription of the conversation. 
+We present a new dataset of human-human task-oriented conversations in the restaurant info domain for supervised training of autonomous systems.
+Currently, the dataset contains only \OP{XY} dialogues because we are still collecting more data, but we estimate that until camera ready deadline we will have more than seven hundreds dialogues.
+We aim at representing the conversation in such way that it is easy to train a system to replace an operator who provides information about the restaurants to clients.
+In contrast to previously released datasets, our dataset contains easy to collect high-quality transcriptions of the client and operator actions during conversations.
+We introduce a~very little overhead by collecting database calls in addition to the transcription of the conversation. 
 In fact, we mimic very closely a~real situation in call centers where operators searches for answers through database user interface. 
@@
 
-Current Spoken Dialogue Systems (SDS) are either handcrafted and use no training data\cite{duvsek2014alex,raux2005let}, but require non-trivial amount of expert work, or are gradually improved from initial policy through live user interaction\cite{young2010hidden,gasic2011line}, and lately are trained using supervised learning typically in end-to-end manner\cite{wen2016network,williams2016end}.\footnote{The~work of \cite{williams2016end} also fine tuned the conversation with reinforcement learning after the supervised-learning stage.}
+Current Spoken Dialogue Systems (SDS) are either handcrafted and use no training data~\cite{duvsek2014alex,raux2005let}, but require non-trivial amount of expert work, or are gradually improved from initial policy through live user interaction~\cite{young2010hidden,gasic2011line}, and lately are trained using supervised learning typically in end-to-end manner~\cite{wen2016network,williams2016end}.\footnote{The~work of \cite{williams2016end} also fine tuned the conversation with reinforcement learning after the supervised-learning stage.}
 The reinforce learning on one hand need just collect enough live user conversation without any transcription with the exception of explicit feedback at the end of each dialogue, but because the feedback signal is typically rather noise and delayed one require thousands of live conversations to improve rather simple policy.\cite{gasic2011line}
@@
 
-We believe that the present dataset can be used for first experiments for end-to-end systems using supervised learning without annotated dialogue state.
-The resulting systems should be able to roughly compare to systems trained on datasets with~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3} dialogue state annotation because the same settings, i.e.\ database and task, for data collection.
-Despite the fact, we collected human-to-human dialogues on known task of Cambridge restaurant domains the data-collecting method is completely domain and language independent.
+We believe that our dataset dataset can be used for first experiments of training end-to-end systems using supervised learning without annotated dialogue state.
+The domain of the dataset is well established thanks to dialogue state tracking (DST) challenges~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3}. 
+The DST challenges proved that the domain is of reasonable complexity.
+In addition, the challenges showed that the DST task is solvable by architectures which may be extended to end-to-end conversational agents~\cite{platek2016recurrent,vodolan2015hybrid,henderson2014word}.
+Note that we collected human-to-human dialogues on Cambridge restaurant domains, but our data-collection method is domain independent.
 
-The paper is structured as follows: The~Section~\ref{sec:repre} motivates the annotations and format of our dataset.
-In the Section~\ref{sec:collection} we introduce our collection process using crowd-sourcing.
-Section~\ref{sec:props} presents the dataset properties and we list the related work in the~Section~\ref{sec:related}.
+The paper is structured as follows: Section~\ref{sec:repre} motivates the annotations and format of our dataset.
+In Section~\ref{sec:collection} we introduce our collection process using crowdsourcing.
+Section~\ref{sec:props} presents the dataset properties and we list the related work in Section~\ref{sec:related}.
 We conclude the paper and suggest future work in~Section~\ref{sec:conc}.
@@
 \label{sec:repre}
-Traditionally, the dialogue systems are designed as pipelines of components, i.e.\ language understanding (LU) unit, dialogue tracker (DT), dialogue manager (DM) and natural language generator (NLG) for chat-based conversational agents.
-If one want to use speech-to-speech conversational agent the 1-best ASR hypothesis can be used as input for LU unit and the NLG can be easily modified so its output is convenient for text-to-speech (TTS) unit which need to appended to the pipeline.
 
-We focus on preparing training data so the LU, DT, DM and NLG components of dialogue system can be trained using such data.
-The TTS and the ASR modules are typically trained with much more data and such data sets are out of scope of this paper.
+We present a dataset for training a task-oriented conversational agent in well defined domain.
+We assume that the agent has a task database\footnote{In the Cambridge restaurant domain the database is a simple table containing information about restaurants.} at hand and plays role of {\it operator}.
+The other interlocutor in the conversation is a~human {\it client}.
+{\it Clients} seek information stored in the database and use the system, which replaced a~human operator, to obtain desired information.
 
-It was shown that few hundreds of annotated domain specific conversation is needed for training relatively well performing LU~\cite{duvsek2014alex} as well as Dialogue State Tracking~\cite{young2010hidden} components.
-The work of~\cite{duvsek2014alex} and~\cite{mairesse2010phrase} showed that also several hundreds of conversations with appropriate annotation is needed for training usable NLG unit on simple domains.
+We focus on data collection for text-to-text task-oriented dialogue systems.
+Traditionally, one would train the pipeline of components of task-oriented dialogue systems, i.e.\ automatic speech recognition (ASR), language understanding (LU) unit, dialogue tracker (DT), dialogue manager (DM), natural language generator (NLG) for text-to-text conversational agents and text-to-speech (TTS) module~\cite{duvsek2014alex}.
+However, typically only the text-to-text pipeline of LU, DT, DM and NLG is trained using just the domain-related text-to-text data~\cite{gasic2011line,jurvcivcek2014factored,duvsek2016sequence}.
+The ASR~\cite{platek2014free} and the TTS~\cite{taylor2009text} modules are typically trained using larger datasets.
+Our datasets contains data for training an~end-to-end system solving task of LU, DT, DM and NLG pipeline of traditional architecture.
+
+% Me to nesedi jako related work - related work je o sbirani dat
+% Tohle me prijde zduvodneni, ze takovy (maly, supervised) dataset dava smysl
+% Zatim nechavam zde: \OD{následující dva odstavce zní dost jako “related work”... možná bych to tam částečně popřesouval? a tady nechal jen ten statement, že stačí málo trénovacích dat?}
+It was shown that few hundreds of annotated domain specific conversations is needed for training relatively well performing LU~\cite{jurvcivcek2014factored} as well as Dialogue State Tracking~\cite{young2010hidden} components.
+The work of~\cite{duvsek2016sequence} and~\cite{mairesse2010phrase} showed that only several hundreds of turns with appropriate annotation is needed for training usable NLG unit on simple domains.
 Even the crucial task of action selection with reward provided only at the end of dialogue can be trained using POMDP dialogue manager and few thousands conversations~\cite{gasic2011line}.
 
-A~novel work of~\cite{wen2016network} showed that only XY conversation annotated with just at dialogue state level is needed for training the whole end-to-end system performing the task of summarizing the dialogue history and reply planning and generation.
-Consequently, we believe that end-to-end systems even with latent variables can be trained using few hundreds conversation if additional supervision in the form of simple annotation is used for narrow goal-oriented domains such as~\cite{wen2016network} domain or Cambridge restaurant domain~\cite{henderson2014dstc2}.
+We believe that end-to-end systems even with latent variables can be trained using few hundreds conversation if additional supervision in the form of simple annotation is used for narrow goal-oriented domains such as~\cite{wen2016network} domain or Cambridge restaurant domain~\cite{henderson2014dstc2}.
+A~recent work of~\cite{wen2016network} showed that only 680 conversation annotated with just at dialogue state level is needed for training the whole end-to-end system performing the task of summarizing the dialogue history and reply planning and generation on a very simple domain.
 
@@
 As a consequence, we see works~\cite{wen2016network,bordes2016learning,williams2016end} as important step forward since there work use annotation only on dialogue state level or even no annotation at all for training dialogue agents.
-
 We believe that annotating a dialogue state according to expert-handcrafted ontology is both an~artificial and a~very labor-intensive data collection task, so our work aim at collecting conversation with lighter but more easier to get annotations.
-We suppose that a task-oriented  domain is defined by a task database\footnote{In the Cambridge restaurant domain the database is a simple table containing information about restaurants.}. 
-We further suppose that there two roles in the conversation a {\it client} and a {\it operator}.
-Typically, one wants to train a system which replaces the {\it operator} who is the domain expert.
-{\it Clients} seek information stored in the database and use the system instead of human operator to obtain desired information.
-We suggest to record conversation between human operator and human clients through crowd-sourcing and by this means collect cheap high quality training data.
+We suggest to record conversation between human operator and human clients through crowdsourcing and by this means collect cheap high quality training data.
 Similar recording setup is known from call centers where the operator is provided with interface to the database so it quickly finds relevant information and plays the role of domain expert.
@@
 
-The calls' to the database when call completely represents the client intention which is the purpose of the dialogue state.
+The calls to the database completely represents the client intention which is the purpose of the dialogue state.
 On the other, the database calls are not present in every turn and thus by logging only the calls one loses a possibility to track partially filled client intention.
 We argue that in high quality human-human conversation there is a minimum turns which are related to the domain and do not contain calls to the database as demonstrated in~Section~\ref{sec:props}.
+It's worth noting that logging operator's database calls in operator-client dialogues is already well established practice in call centers, a~convenient field for commercial application of dialogue systems.
 
@@
 Our data collection processed aimed at collecting natural conversation in the well defined domain.
-We decided to collect new dataset int the~well studied Cambridge restaurant domain since the previous datasets~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3} in that domain demonstrated that a meaningful and not too long conversation can be held in the domain.
-Also it was proven that the domain is on one hand difficult enough that even the state-of-the art systems does not reach human-level performance in the role of the operator and on the other hand numerous systems~\cite{young2010hidden,gasic2011line,wen2016network} demonstrated that are able to provide information to the clients reasonable well.
+We decided to collect new dataset int the~well studied Cambridge restaurant domain since the previous datasets~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3} in that domain demonstrated that a meaningful and of a reasonable length conversation can be held in the domain.
+Also it was proven that the domain is on one hand difficult enough that even the state-of-the art systems does not reach human-level performance in the role of the operator~\cite{henderson2014dstc2} and on the other hand numerous systems~\cite{young2010hidden,gasic2011line,wen2016network} demonstrated that are able to provide information to the clients reasonable well.
 
-We defined our domain by choosing a database from Dialogue State Tracking Challenge 2 (DSTC2)~\cite{henderson2014dstc2} and explaining the interlocutors that there two roles a client and a operator.
-For each conversation we determined goals for the client and provided the database for the operator.
-We used the CrowdFlower (CF) crowd-sourcing platform for collecting the conversations.
+We define our domain by choosing a database from Dialogue State Tracking Challenge 2 (DSTC2)~\cite{henderson2014dstc2}.
+We use the database for steering the dialogue of the two human interlocutors a~{\it client} and an~{\it operator}.
+We use the CrowdFlower (CF) crowdsourcing platform for collecting the conversations.
 
@@
 
-We used exactly the same database as provided for the DSTC2 challenge.
+We used exactly the same database as provided for the DSTC2 challenge~\cite{henderson2014dstc2}.
 The database contains information about 107 restaurants and their properties stored in the columns.
-We include the size of the vocabulary in brackets for each column:
-% \begin{itemize}
-\begin{inparaenum}
+We include in brackets the number of different values for each column:
+\begin{itemize}
+%\begin{inparaenum}
     \item name (107),
-    \item price range (3?),
-    \item area (4),
-    \item food (20?),
-    \item address (90?),
-    \item phone (90?),
-    \item postcode (90?).
-\end{inparaenum}
-% \end{itemize}
+    \item price range (4),
+    \item area (7),
+    \item food (25),
+    \item address (101),
+    \item phone (97),
+    \item postcode (62).
+% \end{inparaenum}\OD{tohle je ošklivý... buď dej do tabulky, nebo vyhoď, pokud by to žralo moc místa (uveď jen souhrnně největší-nejmenší)}
+\end{itemize}
 
-The address or the postcode are unique for each restaurant but are sometimes missing, but the name of the restaurant is always known. 
-There are typically multiple restaurant with the same price range, area, or food type property and these properties might be unknown for a restaurant.
+The address or the phone are unique for each restaurant but are sometimes missing, but the name of the restaurant is always known. 
+There are typically multiple restaurant with the same postcode, price range, area, or food type property and these properties might be unknown for a restaurant.
 
-Note that we use the database to generate the clients goals as demonstrated in~Figure~\ref{fig:client} and only the operator is able to search the database add demonstrated in~Figure~\ref{fig:operator}.
+We use the database to generate client goals for CF users (see Figure~\ref{fig:client}), and CF users playing role of the operator can directly access and search the database (see Figure~\ref{fig:operator}).
 
@@
 He may choose not to seek the goal immediately but submit more appropriate response such as greeting first.
-The goals for the client are presented to the CF workers gradually and may contradict each other.
+The goals are displayed to the CF worker in the client role gradually turn-by-turn and the goals may contradict each other.
 For example, the client may at first want a Chinese food, but later it changes her mind and wants to find restaurant serving British food.
 
-Before submitting a reply the client is instructed to read the dialogue history and marked the goals which were presented to the operator.
+Before submitting a reply the client is instructed to read the dialogue history and marked the goals which were presented to the operator as demonstrated in Figure~\ref{fig:client}.
+By marking which goals have been already presented to the operator we force the CF workers to pay attention to the dialogue history before submitting their reply.
+In Section~\ref{sec:async} we describe how we combine the workers replies to conversations.
 
@@
 The CF workers are also instructed also explicitly mark the rows of the restaurants about which provide the information in their answer.
+Similarly to the client role, an operator does not have to reply to all requested information at once.
+It is up to worker which information is provided first.
+
+The full text search, our interface to the database, is implemented in Javascript as a simple substring matching over values in the database.
+Multiple constrains can be expressed by two substrings separated by a comma.
+We used such a simple interface because it is easy to generate the candidate results given the query and the database.
+The CF workers were instructed to mark a candidate row from the results about which they inform in their reply.
 
@@
 \includegraphics[height=25em]{gui-annotators-system}
-\caption{Operator annotation interface}
+\caption{Operator annotation interface}\OD{v obrázcích bych se snažil nějak zvětšit text (menší okno prohlížeče před printscreenem? nějak upravené CSS? nevím... zas to asi nesmí být moc práce)}
 \end{center}
@@
 \label{sec:async}
-We design the crowd-sourcing jobs so the CF contributors are able to work independently to each other.
+We design the crowdsourcing jobs so the CF contributors are able to work independently to each other.
 The roles of client and operator take turns as sets of partial conversations are submitted for collecting a single new response.
@@
 
-Each utterance in conversation is submitted by different contributor, so contributors need to read carefully the dialogue history to understand the conversation before submitting their response.
+Each utterance in conversation may be submitted by different contributor, so contributors need to read carefully the dialogue history to understand the conversation before submitting their response.
 The workers are able to mark dialogues which does not make sense and thus they self-assess quality of the conversations.
@@
 
-We bootstrap the conversation either with an operators introduction "{\it Hello , welcome to the Cambridge restaurant system?
-You can ask for restaurants by area , price range or food type .
-How may I help you?}" or we bootstrap the conversation with a~full turn where we add clients greeting e.g.
+We bootstrap the conversation either with an operators introduction "{\it Hello , welcome to the Cambridge restaurant system...}" or we bootstrap the conversation with a~full turn where we add clients greeting e.g.
 {\it "Hi"} to aforementioned operators utterance.
@@
 In single job submission we let the workers append to each dialogue a~single response.
-Typically, we submit from twenty to thirty partial dialogues with different history lengths.
-Some conversations might be just initialized with the auto-generated greetings but most of them store multiple turns collected by CF contributors in the~previous submission.
+% Typically, we submit for annotation from twenty to thirty partial dialogues with different history lengths.
+%Some conversations might be just initialized with the auto-generated greetings but most of them store multiple turns collected by CF contributors in the~previous submission.
+% \OD{od “typically...” mi to přijde jako technikálie, která spíš mate}
 Note also that the conversations are typically rather short so full dialogues are collected after few rounds of submissions.
@@
 We collected XY conversation with average length ZY.
-During an average conversation 2.4-TODO tasks are requested and answered.
-Typically in 65-TODO \% case the conversation is ended by the client
-As we mention the conversation are short, taking only from {\bf TODO} four to six turns including first turn with greetings.
+During an average conversation \OP{2.4} tasks are requested and answered.
+Typically in \OP{65} \% case the conversation is ended by the client
+As we mention the conversation are short, taking only from \OP{four to six turns} including first turn with greetings.
 \begin{table}
@@
 
-During the data collection process we discarded roughly 40-TODO \% of conversation in total.
-We split the XYZ collected conversation randomly into training, development and test set (see Table~\ref{tab:props}).
+During the data collection process we discarded roughly \OP{40} \% of conversation.
+We split the \OP{XYZ} collected conversation randomly into training, development and test set (see Table~\ref{tab:props}).
 
@@
 
-A~relevant work of~\cite{wen2016network} collected human-human dialogues in similar domain to the Cambridge domain according their description.
+A~relevant work of~\cite{wen2016network} collected human-human dialogues in similar but more restricted domain than the Cambridge domain.
 Their dataset is not yet published so we compare only with their statistics.
 The dataset is of similar size and used very similar collection scheme where the Amazon Mechanical Turk workers submitted one reply at a time without being connected to each other in real-time.
+On the other, hand they collected explicit dialogue state annotation which takes significant annotation effort.
 
@@
 
-There is significant amount of work which used Wizard of Oz experiments~\cite{whittaker2002fish,walker1997evaluating,rieser2008learning} for studying linguistic properties of dialogues, evaluating proof of concept or even collecting bootstrap training data, but according our knowledge no other work than~\cite{wen2016network} have not used cheap crowd-sourcing workers to collect a~full training dataset for supervised learning.
+There is significant amount of work which used Wizard of Oz experiments~\cite{whittaker2002fish,walker1997evaluating,rieser2008learning} for studying linguistic properties of dialogues, evaluating proof of concept or even collecting bootstrap training data, but according our knowledge no other work than~\cite{wen2016network} have not used cheap crowdsourcing workers to collect a~full training dataset for supervised learning of dialogue management or end-to-end conversations.
 
@@
 We present a new human-human dialogue dataset with annotation of user intention in form of their database calls.
-We also introduced a novel data collection setting which resembles work of operators in call centers and introduce minimum overhead to crowd-sourcing workers.
+We also introduced a novel data collection setting which resembles work of operators in call centers and introduce minimum overhead to crowdsourcing workers.
+% TO mi prijde ze v call -centrech delaji stejne\OD{, apart from stating their replies in natural language (?)}
 The collected dialogues are published under Creative Commons 4.0 BY-SA license on available to download at {\it anonymized}.  % lindat\footnote{todo where}.
 
-We plan to increase the number of collected dialogues till the camera ready deadline to XYZU.
+We plan to increase the number of collected dialogues till the camera ready deadline to \OP{XYZU}.
 We intend to use the dataset to train and evaluate an~end-to-end conversational model which uses only the database calls as additional supervision to the recorded responses.
@@
 \subsubsection*{Acknowledgments}
-We would like to thank Ond\v{r}ej Du\v{s}ek for useful comments.
+We would like to thank Ondřej Dušek for useful comments.
 This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333.

### 2016-06-28 paper.tex
Update on Overleaf.
dataset description

@@
 \maketitle
-
 \OP{Fill missing values about the dataset collected so far} \\
-\OP{describe the dataset,apologize for not having the dataset collected - promise for camera ready version.} \\
+\OP{new client interface image so the text is visible, fit to 8 pages}
 \OP{grammar check} \\
@@
 We present a new dataset of human-human task-oriented conversations in the restaurant info domain for supervised training of autonomous systems. 
-Currently, the dataset contains only \OP{XY} dialogues because we are still collecting more data, but we estimate that until camera ready deadline we will have more than seven hundreds dialogues.
+Currently, the dataset contains only \OP{62} dialogues because we are still collecting more data, but we estimate that until camera ready deadline we will have more than seven hundreds dialogues. 
 We aim at representing the conversation in such way that it is easy to train a system to replace an operator who provides information about the restaurants to clients.
@@
 We include in brackets the number of different values for each column:
-\begin{itemize}
-%\begin{inparaenum}
+\begin{itemize}  % tabulku misto tohohle?
     \item name (107),
@@
     \item postcode (62).
-% \end{inparaenum}\OD{tohle je ošklivý... buď dej do tabulky, nebo vyhoď, pokud by to žralo moc místa (uveď jen souhrnně největší-nejmenší)}
 \end{itemize}
@@
 \begin{center}
-\includegraphics[height=25em]{gui-annotators-client}
+\includegraphics[height=30em]{gui-annotators-client}
 \caption{Client annotation interface}
@@
 \begin{center}
-\includegraphics[height=25em]{gui-annotators-system}
-\caption{Operator annotation interface}\OD{v obrázcích bych se snažil nějak zvětšit text (menší okno prohlížeče před printscreenem? nějak upravené CSS? nevím... zas to asi nesmí být moc práce)}
+\includegraphics[height=35em]{gui-annotators-system}
+\caption{Operator annotation interface}
 \end{center}
@@
 In single job submission we let the workers append to each dialogue a~single response.
-% Typically, we submit for annotation from twenty to thirty partial dialogues with different history lengths.
-%Some conversations might be just initialized with the auto-generated greetings but most of them store multiple turns collected by CF contributors in the~previous submission.
-% \OD{od “typically...” mi to přijde jako technikálie, která spíš mate}
 Note also that the conversations are typically rather short so full dialogues are collected after few rounds of submissions.
@@
 
-% TODO describe how we started with 5 bootstrapped conversation with client role 5 without it and then mixed the partial with new one and resubmit them until the first conversations were marked as finished.
-
 \section{Dataset Properties}
@@
 
-We collected XY conversation with average length ZY.
-During an average conversation \OP{2.4} tasks are requested and answered.
-Typically in \OP{65} \% case the conversation is ended by the client
-As we mention the conversation are short, taking only from \OP{four to six turns} including first turn with greetings.
-\begin{table}
-\begin{center}
-\begin{tabular}{lrr}
-\hline
-Set   & \# Dialogues & \# Turns \\
-\hline
-% Joint  &  todo &  todo \\
-% /a/SSD/oplatek/e2end/log/2016-06-08-17-31-38.400-dstc-INDEP_labels-d0.7-w100-e100/
-% /a/SSD/oplatek/e2end/log/TEST-ORIGINAL-2016-06-08-17-31-38.400dstc-INDEP_labels-d0.7-w100-e100-reward-0.9080-step-0036224
-Train  &   ? & ? \\
-Dev &   ? & ? \\
-Test &   ? & ? \\
-\hline
-\end{tabular}
-\caption{Accuracy on development and test set}
-\vspace{-2em}
-\end{center}
-\label{tab:props}
-\end{table}
+We just started to collect our dataset and so far we collected only 60 conversations.
+The average length of a conversation is \OP{3.8} turns, meaning that the contributors and in both roles reply three times before the conversation is finished\footnote{First system reply is automatically generated and for some conversation even the first client reply is also initialized as described in Section~\ref{sec:async}}.
+During an average conversation \OP{2.4} tasks are requested and \OP{1.9} answered.
+Typically in \OP{65} \% case the conversation is ended by the client.
+% As we mention the conversation are short, taking only from \OP{four to six turns} including first turn with greetings.
+% \begin{table}
+% \begin{center}
+% \begin{tabular}{lrr}
+% \hline
+% Set   & \# Dialogues & \# Turns \\
+% \hline
+% % Joint  &  todo &  todo \\
+% % /a/SSD/oplatek/e2end/log/2016-06-08-17-31-38.400-dstc-INDEP_labels-d0.7-w100-e100/
+% % /a/SSD/oplatek/e2end/log/TEST-ORIGINAL-2016-06-08-17-31-38.400dstc-INDEP_labels-d0.7-w100-e100-reward-0.9080-step-0036224
+% Train  &   ? & ? \\
+% Dev &   ? & ? \\
+% Test &   ? & ? \\
+% \hline
+% \end{tabular}
+% \caption{Accuracy on development and test set}
+% \vspace{-2em}
+% \end{center}
+% \label{tab:props}
+% \end{table}
 
-During the data collection process we discarded roughly \OP{40} \% of conversation.
-We split the \OP{XYZ} collected conversation randomly into training, development and test set (see Table~\ref{tab:props}).
+During the data collection process we discarded over \OP{40} \% of conversation because one of the utterances were mark as low quality.
+Note that we discard only the low quality utterance and sufix of that conversation, the prefix is submitted for finishing the conversation in next rounds of jobs.
+Once we will collect enough conversation we intend to split them into training, development and test set. % (see Table~\ref{tab:props}).
 
@@
 
-We plan to increase the number of collected dialogues till the camera ready deadline to \OP{XYZU}.
+We plan to increase the number of collected dialogues till the camera ready deadline to 700 or more.
 We intend to use the dataset to train and evaluate an~end-to-end conversational model which uses only the database calls as additional supervision to the recorded responses.

### 2016-06-28 paper.tex
Update on Overleaf.

--- 2016-06-27 paper.tex
@@
 \maketitle
-
 \OP{Fill missing values about the dataset collected so far} \\
-\OP{describe the dataset,apologize for not having the dataset collected - promise for camera ready version.} \\
+\OP{describe the dataset,apologize for not having the dataset collected - promise for camera ready version.} \OD{You don't need to apologize, just state that.
+You can, but don't need to say how many you currently have}\\
 \OP{grammar check} \\

### 2016-06-28 paper.tex
fit on 9 pages including references

--- 2016-06-28 paper.tex
@@
 
-\def\OP#1{{\color{red}OP: \it #1}}
-\def\ODdel#1{\bgroup\markoverwith{\textcolor{red}{\rule[0.5ex]{2pt}{1pt}}}\ULon{#1}}
+% \def\OP#1{{\color{red}OP: \it #1}}
+% \def\ODdel#1{\bgroup\markoverwith{\textcolor{red}{\rule[0.5ex]{2pt}{1pt}}}\ULon{#1}}
+\def\OP#1{#1}  % do nothing - disable the comments in whole documment
 
@@
 \maketitle
-\OP{Fill missing values about the dataset collected so far} \\
-\OP{new client interface image so the text is visible, fit to 8 pages}
-\OP{grammar check} \\
+% \OP{Fill missing values about the dataset collected so far} \\
+% \OP{grammar check} \\
 
@@
 
+\vspace{-1.00em}
 \keywords{task-oriented dialogue, end-to-end, dataset}
+\vspace{-1.00em}
 
@@
 \section{Introduction}\label{sec:intro}
+\vspace{-0.50em}
 We present a new dataset of human-human task-oriented conversations in the restaurant info domain for supervised training of autonomous systems. 
@@
 Current Spoken Dialogue Systems (SDS) are either handcrafted and use no training data~\cite{duvsek2014alex,raux2005let}, but require non-trivial amount of expert work, or are gradually improved from initial policy through live user interaction~\cite{young2010hidden,gasic2011line}, and lately are trained using supervised learning typically in end-to-end manner~\cite{wen2016network,williams2016end}.\footnote{The~work of \cite{williams2016end} also fine tuned the conversation with reinforcement learning after the supervised-learning stage.}
-The reinforce learning on one hand need just collect enough live user conversation without any transcription with the exception of explicit feedback at the end of each dialogue, but because the feedback signal is typically rather noise and delayed one require thousands of live conversations to improve rather simple policy.\cite{gasic2011line}
+The reinforcement learning need just collect enough live user conversation containing only explicit feedback, but because the feedback signal is typically simple, noisy and delayed one require thousands of live conversations to improve rather simple policy.\cite{gasic2011line}
 The supervised-learning methods greatly reduced the number of conversation needed for training reasonable policy to few hundreds\cite{wen2016network}, but require annotation for all components used the dialogue which so far included at least a dialogue state\cite{wen2016network,young2010hidden}.
@@
 
-\section{Supervised feedback for task-oriented dialogue}
-\label{sec:repre}
-
+\section{Supervised feedback for task-oriented dialogue} \label{sec:repre}
+\vspace{-0.50em}
 We present a dataset for training a task-oriented conversational agent in well defined domain.
@@
 We note that further annotation of dialogue conversation may help to train the models faster, but simply collecting more data is typically more beneficial.
-As a consequence, we see works~\cite{wen2016network,bordes2016learning,williams2016end} as important step forward since there work use annotation only on dialogue state level or even no annotation at all for training dialogue agents.
+As a consequence, we see works~\cite{wen2016network,bordes2016learning,williams2016end} as important step forward not to rely on rich annotations for training dialogue agents.
 We believe that annotating a dialogue state according to expert-handcrafted ontology is both an~artificial and a~very labor-intensive data collection task, so our work aim at collecting conversation with lighter but more easier to get annotations.
@@
 
-\section{Dataset Collection Process}
-\label{sec:collection}
-
+\section{Dataset Collection Process} \label{sec:collection}
+\vspace{-0.50em}
 Our data collection processed aimed at collecting natural conversation in the well defined domain.
@@
 
+\vspace{-1.00em}
 \subsection{Domain database}
@@
 We include in brackets the number of different values for each column:
+\vspace{-0.50em}
 \begin{itemize}  % tabulku misto tohohle?
@@
 \end{itemize}
+\vspace{-0.50em}
 
@@
 
+\vspace{-1.00em}
 \subsection{Client interface}
@@
 \begin{figure}
+\vspace{-1.00em}
 \begin{center}
@@
 \end{center}
-\vspace{-0.80em}
+\vspace{-1.00em}
 \label{fig:client}
 \end{figure}
+\vspace{-1.00em}
 
+\vspace{-1.00em}
 \subsection{Operator interface}
@@
 \end{center}
-\vspace{-0.80em}
+\vspace{-1.00em}
 \label{fig:operator}
 \end{figure}
+\vspace{-1.00em}
 
+\vspace{-1.00em}
 \subsection{Asynchronous collection without real-time responses}
@@
 
-\section{Dataset Properties}
-\label{sec:props}
-
+\section{Dataset Properties} \label{sec:props}
+\vspace{-0.50em}
 We just started to collect our dataset and so far we collected only 60 conversations.
@@
 During an average conversation \OP{2.4} tasks are requested and \OP{1.9} answered.
-Typically in \OP{65} \% case the conversation is ended by the client.
+% Typically in \OP{65} \% case the conversation is ended by the client.
 % As we mention the conversation are short, taking only from \OP{four to six turns} including first turn with greetings.
@@
 % \end{table}
-
-During the data collection process we discarded over \OP{40} \% of conversation because one of the utterances were mark as low quality.
-Note that we discard only the low quality utterance and sufix of that conversation, the prefix is submitted for finishing the conversation in next rounds of jobs.
+During the data collection process we discarded over \OP{20} \% of replies because the utterances were of low quality.
+Note that we discard only the low quality utterance, the prefix of the conversation is submitted for finishing the conversation in next rounds of jobs.
 Once we will collect enough conversation we intend to split them into training, development and test set. % (see Table~\ref{tab:props}).
 
-\section{Related Work}
-\label{sec:related}
-
+\section{Related Work} \label{sec:related}
+\vspace{-0.50em}
 Our work is closely related  to work of~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3} in the sense that the conversation are held in the same domain.
@@
 
-\section{Conclusion and Future work}
-\label{sec:conc}
+\section{Conclusion and Future work} \label{sec:conc}
+\vspace{-0.50em}
 We present a new human-human dialogue dataset with annotation of user intention in form of their database calls.
@@
 
+\vspace{-1.00em}
 \subsubsection*{Acknowledgments}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{-1.00em}
 \bibliographystyle{splncs03}
 \bibliography{paper}
+\vspace{-1.00em}
 
-All links were last followed on June 28, 2016.
+% All links were last followed on June 28, 2016.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-06-28 paper.tex
fit 9 pages included references
submitted version - todo preprint oplatek sds
change title

@@
 
-\title{Dataset of operator-client dialogues aligned with knowledge-base queries}
+\title{Dataset of operator-client dialogues aligned with database queries}
 
@@
  	The dataset is collected using crowdsourcing on well known restaurant domain.
-    The quality of the data is enforced by mutual control among contributors and manually verified on random sub-sample.
+    The quality of the data is enforced by mutual control among contributors.  % TODO and manually verified on random sub-sample 
     The dataset is available for download under the Creative Commons 4.0 BY-SA license.
@@
 
-\vspace{-1.00em}
+\vspace{-1.40em}
 \subsubsection*{Acknowledgments}
@@
 \bibliography{paper}
-\vspace{-1.00em}
 

### 2016-06-28 paper.tex
minor corrections

@@
 We present a new dataset of human-human task-oriented conversations in the restaurant info domain for supervised training of autonomous systems. 
-Currently, the dataset contains only \OP{62} dialogues because we are still collecting more data, but we estimate that until camera ready deadline we will have more than seven hundreds dialogues. 
+Currently, the dataset contains only \OP{62} dialogues because we are still collecting more data, but we estimate we will have more than 700 dialogues until the camera ready deadline.
+
 We aim at representing the conversation in such way that it is easy to train a system to replace an operator who provides information about the restaurants to clients.
@@
 On the other hand, just logging the calls to the task database provide us with information of the similar quality as it is contained in manually annotated dialogue state, just not annotated incrementally after each turn.
-Tracking the database calls in task oriented systems together with conversation transcription should not introduce much overhead during data collection, but should presumably boost end-to-end conversational agent as much as annotated dialogue state when training with such data.
+Tracking the database calls in task oriented systems together with conversation transcription should not introduce significant overhead during data collection, but should presumably boost end-to-end conversational agent as much as annotated dialogue state when training with such data.
 
@@
 Since the dialogue state is simplification of dialogue history and has no broadly-accepted form, it is very expensive to collect such annotated data because the dialogue state typically differs among domains and its structure is hard to explain to annotators.
-In this paper, we focus on collecting supervised training set with rich enough annotation so the supervised models similar to~\cite{wen2016network} can be trained with few hundreds of dialogues, but the annotation of dialogues are much easier to collect.
+In this paper, we focus on collecting supervised training set with rich enough annotation so the supervised models similar to~\cite{wen2016network} can be trained with few hundreds of dialogues, but the annotation of dialogues are easier to collect.
 

### 2016-06-28 paper.tex
lexical fixes

@@
     This paper presents a novel dataset for training end-to-end task oriented conversational agents.
-    The dataset contains task oriented conversations between an operator – a task expert, and a client who is seeking information about the task, along with records of database API calls performed by the operator, which capture the distilled meaning of the user query.
-    We expect that thanks to this easy-to-get supervision of database calls one would require significantly less training data for training end-to-end dialogue agents.
- 	The dataset is collected using crowdsourcing on well known restaurant domain.
+    The dataset contains conversations between an operator – a task expert, and a client who seeks information about the task.
+    Along with the conversation transcriptions we record database API calls performed by the operator, which capture the distilled meaning of the user query.
+    We expect that the easy-to-get supervision of database calls allow to train end-to-end dialogue agents with significantly less training data.
+ 	The dataset is collected using crowdsourcing and the conversations cover well known restaurant domain.
     The quality of the data is enforced by mutual control among contributors.  % TODO and manually verified on random sub-sample 
@@
 In fact, we mimic very closely a~real situation in call centers where operators searches for answers through database user interface. 
-On the other hand, just logging the calls to the task database provide us with information of the similar quality as it is contained in manually annotated dialogue state, just not annotated incrementally after each turn.
+Just logging the calls to the task database provide us with information of the similar quality as it is contained in manually annotated dialogue state, but not annotated incrementally after each turn.
 Tracking the database calls in task oriented systems together with conversation transcription should not introduce significant overhead during data collection, but should presumably boost end-to-end conversational agent as much as annotated dialogue state when training with such data.
@@
 Current Spoken Dialogue Systems (SDS) are either handcrafted and use no training data~\cite{duvsek2014alex,raux2005let}, but require non-trivial amount of expert work, or are gradually improved from initial policy through live user interaction~\cite{young2010hidden,gasic2011line}, and lately are trained using supervised learning typically in end-to-end manner~\cite{wen2016network,williams2016end}.\footnote{The~work of \cite{williams2016end} also fine tuned the conversation with reinforcement learning after the supervised-learning stage.}
-The reinforcement learning need just collect enough live user conversation containing only explicit feedback, but because the feedback signal is typically simple, noisy and delayed one require thousands of live conversations to improve rather simple policy.\cite{gasic2011line}
-The supervised-learning methods greatly reduced the number of conversation needed for training reasonable policy to few hundreds\cite{wen2016network}, but require annotation for all components used the dialogue which so far included at least a dialogue state\cite{wen2016network,young2010hidden}.
+The reinforcement learning need just collect enough live user conversation containing only explicit feedback.
+However, the feedback signal is harder to interpret than supervised annotation one require thousands of live conversations to improve rather simple policy.\cite{gasic2011line}
+The supervised-learning methods greatly reduced the number of conversation needed for training reasonable policy to few hundreds\cite{wen2016network}, but require annotation for all components used in the dialogue system.
+According to our knowledge the system require annotation at least for a dialogue state\cite{wen2016network,young2010hidden}.
 Since the dialogue state is simplification of dialogue history and has no broadly-accepted form, it is very expensive to collect such annotated data because the dialogue state typically differs among domains and its structure is hard to explain to annotators.
@@
 The work of~\cite{duvsek2016sequence} and~\cite{mairesse2010phrase} showed that only several hundreds of turns with appropriate annotation is needed for training usable NLG unit on simple domains.
-Even the crucial task of action selection with reward provided only at the end of dialogue can be trained using POMDP dialogue manager and few thousands conversations~\cite{gasic2011line}.
+Even the crucial task of action selection can be trained using POMDP dialogue manager and few thousands conversations despite the fact that rewards are provided only at the end of dialogue~\cite{gasic2011line}.
 
-We believe that end-to-end systems even with latent variables can be trained using few hundreds conversation if additional supervision in the form of simple annotation is used for narrow goal-oriented domains such as~\cite{wen2016network} domain or Cambridge restaurant domain~\cite{henderson2014dstc2}.
-A~recent work of~\cite{wen2016network} showed that only 680 conversation annotated with just at dialogue state level is needed for training the whole end-to-end system performing the task of summarizing the dialogue history and reply planning and generation on a very simple domain.
+We believe that end-to-end systems even can be trained using few hundreds conversation if additional supervision in the form of simple annotation is used for narrow goal-oriented domains such as Cambridge restaurant domain~\cite{henderson2014dstc2} or its simplification~\cite{wen2016network}.
+The~work of~\cite{wen2016network} showed that only 680 conversations annotated just at dialogue state level are needed for training the complete end-to-end system performing the task of summarizing the dialogue history, response planning and generation.
 
-We note that further annotation of dialogue conversation may help to train the models faster, but simply collecting more data is typically more beneficial.
-As a consequence, we see works~\cite{wen2016network,bordes2016learning,williams2016end} as important step forward not to rely on rich annotations for training dialogue agents.
-We believe that annotating a dialogue state according to expert-handcrafted ontology is both an~artificial and a~very labor-intensive data collection task, so our work aim at collecting conversation with lighter but more easier to get annotations.
+We realise that further annotation of dialogue conversation may help to train the models faster, but simply collecting more data is typically more beneficial.
+As a consequence, we see works~\cite{wen2016network,bordes2016learning,williams2016end} as important step forward to reducing the need of rich annotations for training dialogue agents.
+We believe that annotating a dialogue state according to expert-handcrafted ontology is both an~artificial and a~very labor-intensive data collection task, so our work aim at collecting conversation with lighter and more easier to get annotations.
 We suggest to record conversation between human operator and human clients through crowdsourcing and by this means collect cheap high quality training data.
 Similar recording setup is known from call centers where the operator is provided with interface to the database so it quickly finds relevant information and plays the role of domain expert.
-We suggest to collect the operator's database calls with its arguments instead of dialogue state annotation after each turn.
+For our dataset, we collect the operator's database calls with its arguments instead of dialogue state annotation after each turn.
 
@@
 
-We use the database to generate client goals for CF users (see Figure~\ref{fig:client}), and CF users playing role of the operator can directly access and search the database (see Figure~\ref{fig:operator}).
+We use the database to generate client goals for CF users (see Figure~\ref{fig:client}).
+The database was also available to CF users playing role of the operator through a simple interface (see Figure~\ref{fig:operator}).
 
@@
 
-The client is given a goal to request provided information from the operator.
-He may choose not to seek the goal immediately but submit more appropriate response such as greeting first.
+The client is asked to request a specific information - a goal from the operator.
+He may choose not to seek the goal immediately but submit more appropriate response such as greeting instead.
 The goals are displayed to the CF worker in the client role gradually turn-by-turn and the goals may contradict each other.
@@
 By marking which goals have been already presented to the operator we force the CF workers to pay attention to the dialogue history before submitting their reply.
-In Section~\ref{sec:async} we describe how we combine the workers replies to conversations.
+In Section~\ref{sec:async} we describe how we combine the workers replies to form a~conversations.
 
@@
 The content of the database is intentional hidden if no filter is specified so the filter has to be used.
-The CF workers are also instructed also explicitly mark the rows of the restaurants about which provide the information in their answer.
+The CF workers are also instructed explicitly mark the rows of the restaurants about which provide the information in their answer.
 Similarly to the client role, an operator does not have to reply to all requested information at once.
-It is up to worker which information is provided first.
+It is up to the~worker which information is provided first.
 
@@
 Multiple constrains can be expressed by two substrings separated by a comma.
-We used such a simple interface because it is easy to generate the candidate results given the query and the database.
+We used such a simple interface because it is easy to generate and also reconstruct the candidate results given the query and the database.
 The CF workers were instructed to mark a candidate row from the results about which they inform in their reply.
@@
 The roles of client and operator take turns as sets of partial conversations are submitted for collecting a single new response.
-As a consequence, multiple contributors participate in submitting responses for single conversation for both roles.
+As a consequence, a~single conversation is collected from multiple contributors over several job submissions.
 
@@
 {\it "Hi"} to aforementioned operators utterance.
-If we initialize the dialogue with a~full turn the first contributor plays role of the system if we bootstrap the conversation only with~the operators greeting, the contributors plays the client's role.
+If we initialize the dialogue with a~full turn the first contributor plays role of the system if we bootstrap the conversation only with~the operators greeting, the contributor plays the client's role.
 
-In single job submission we let the workers append to each dialogue a~single response.
+In a~single job submission, we let the workers append to each dialogue a~single response.
 Note also that the conversations are typically rather short so full dialogues are collected after few rounds of submissions.
@@
 We just started to collect our dataset and so far we collected only 60 conversations.
-The average length of a conversation is \OP{3.8} turns, meaning that the contributors and in both roles reply three times before the conversation is finished\footnote{First system reply is automatically generated and for some conversation even the first client reply is also initialized as described in Section~\ref{sec:async}}.
+The average length of a conversation is \OP{3.8} turns, meaning that the contributors in both roles reply in average circa three times before the conversation is finished\footnote{First system reply is automatically generated and for some conversation even the first client reply is also initialized as described in Section~\ref{sec:async}}.
 During an average conversation \OP{2.4} tasks are requested and \OP{1.9} answered.
@@
 % \end{table}
-During the data collection process we discarded over \OP{20} \% of replies because the utterances were of low quality.
+During the data collection process we discarded over \OP{35} \% of replies because the utterances were of low quality.
 Note that we discard only the low quality utterance, the prefix of the conversation is submitted for finishing the conversation in next rounds of jobs.
@@
 Our work is closely related  to work of~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3} in the sense that the conversation are held in the same domain.
-On the other hand, the collection process differs substantially because we do not use any artificial system and rather we focus on collecting high quality human conversations.
+On the other hand, the collection process differs substantially because we do not use any artificial system in the operator's role.  
+We rather focus on collecting high quality human conversations. 
 In addition, in our work we do not collect complicated annotations on LU and DST level.
@@
 Their dataset is not yet published so we compare only with their statistics.
-The dataset is of similar size and used very similar collection scheme where the Amazon Mechanical Turk workers submitted one reply at a time without being connected to each other in real-time.
-On the other, hand they collected explicit dialogue state annotation which takes significant annotation effort.
+The dataset is of similar size as we intend to collect and a~very similar collection scheme was used where Amazon Mechanical Turk workers submitted one reply at a time without being connected to each other in real-time.
+On the other hand, they collected explicit dialogue state annotation which takes significant annotation effort.
 
@@
 
-There is significant amount of work which used Wizard of Oz experiments~\cite{whittaker2002fish,walker1997evaluating,rieser2008learning} for studying linguistic properties of dialogues, evaluating proof of concept or even collecting bootstrap training data, but according our knowledge no other work than~\cite{wen2016network} have not used cheap crowdsourcing workers to collect a~full training dataset for supervised learning of dialogue management or end-to-end conversations.
+There is a~significant amount of work which used Wizard of Oz experiments~\cite{whittaker2002fish,walker1997evaluating,rieser2008learning} for studying linguistic properties of dialogues, evaluating proof of concept or even collecting bootstrap training data, but according our knowledge no other work than~\cite{wen2016network} have used cheap crowdsourcing workers to collect a~full training dataset for supervised learning of dialogue management or end-to-end conversations.
 
@@
 \vspace{-0.50em}
-We present a new human-human dialogue dataset with annotation of user intention in form of their database calls.
+We present a new human-human dialogue dataset with annotation of user intention in form of operator's database calls.
 We also introduced a novel data collection setting which resembles work of operators in call centers and introduce minimum overhead to crowdsourcing workers.

### 2016-06-28 paper.tex
use 62 instead of 62 and 60 conversations
Intro

@@
 
-\title{Dataset of operator-client dialogues aligned with database queries}
+\title{A Dataset of Operator-client Dialogues Aligned with Database Queries}
 
@@
 % \OP{grammar check} \\
+\OD{Přemýšlím, jestli ten název neudělat nějak míň popisný a víc vysvětlující (něco o end-to-end dialogue systems)?}
 
@@
     The dataset contains conversations between an operator – a task expert, and a client who seeks information about the task.
-    Along with the conversation transcriptions we record database API calls performed by the operator, which capture the distilled meaning of the user query.
-    We expect that the easy-to-get supervision of database calls allow to train end-to-end dialogue agents with significantly less training data.
- 	The dataset is collected using crowdsourcing and the conversations cover well known restaurant domain.
-    The quality of the data is enforced by mutual control among contributors.  % TODO and manually verified on random sub-sample 
+    Along with the conversation transcriptions, we record database API calls performed by the operator, which capture a distilled meaning of the user query.
+    We expect that the easy-to-get supervision of database calls will allow us to train end-to-end dialogue agents with significantly less training data.
+ 	The dataset is collected using crowdsourcing and the conversations cover the well-known restaurant domain.
+    Quality of the data is enforced by mutual control among contributors.  % TODO and manually verified on random sub-sample 
     The dataset is available for download under the Creative Commons 4.0 BY-SA license.
@@
 \vspace{-0.50em}
-We present a new dataset of human-human task-oriented conversations in the restaurant info domain for supervised training of autonomous systems. 
+We present a new dataset of human-human task-oriented conversations in the restaurant information domain, suitable for supervised training of autonomous systems. 
 Currently, the dataset contains only \OP{62} dialogues because we are still collecting more data, but we estimate we will have more than 700 dialogues until the camera ready deadline.
+\OD{We are currently collecting data for the set using crowdsourcing.
+We have collected 62 dialogues so far; more than 700 dialogues are planned for the final version of the dataset.\footnote{\OD{We expect to release the set before the camera-ready deadline.}}}
 
-We aim at representing the conversation in such way that it is easy to train a system to replace an operator who provides information about the restaurants to clients.
-In contrast to previously released datasets, our dataset contains easy to collect high-quality transcriptions of the client and operator actions during conversations.
+We aim at representing the conversation in a way that makes it easy to train an automated system to replace a human operator. 
+In contrast to previously released datasets, our dataset contains easy-to-collect high-quality transcriptions of the client and operator actions during conversations.\OD{tady úplně nevím, k čemu se kontrastuješ}
 We introduce a~very little overhead by collecting database calls in addition to the transcription of the conversation.
-In fact, we mimic very closely a~real situation in call centers where operators searches for answers through database user interface. 
-Just logging the calls to the task database provide us with information of the similar quality as it is contained in manually annotated dialogue state, but not annotated incrementally after each turn.
-Tracking the database calls in task oriented systems together with conversation transcription should not introduce significant overhead during data collection, but should presumably boost end-to-end conversational agent as much as annotated dialogue state when training with such data.
+In fact, we mimic very closely a~real situation in call centers where operators search for answers through a database user interface. 
+Just logging the calls to the task database provide us with information of a similar quality as a full manual dialogue state annotation, but not annotated incrementally after each turn.\OD{od “but” nerozumím}
+Tracking the database calls in task oriented systems together with conversation transcription should not introduce significant overhead during the data collection, but should presumably boost end-to-end conversational agent as much as annotated dialogue state when training with such data.\OD{but should provide a similar amount of supervision for training an end-to-end conversational agent as using fully annotated dialogue state ??}
 
-Current Spoken Dialogue Systems (SDS) are either handcrafted and use no training data~\cite{duvsek2014alex,raux2005let}, but require non-trivial amount of expert work, or are gradually improved from initial policy through live user interaction~\cite{young2010hidden,gasic2011line}, and lately are trained using supervised learning typically in end-to-end manner~\cite{wen2016network,williams2016end}.\footnote{The~work of \cite{williams2016end} also fine tuned the conversation with reinforcement learning after the supervised-learning stage.}
-The reinforcement learning need just collect enough live user conversation containing only explicit feedback.
-However, the feedback signal is harder to interpret than supervised annotation one require thousands of live conversations to improve rather simple policy.\cite{gasic2011line}
-The supervised-learning methods greatly reduced the number of conversation needed for training reasonable policy to few hundreds\cite{wen2016network}, but require annotation for all components used in the dialogue system.
-According to our knowledge the system require annotation at least for a dialogue state\cite{wen2016network,young2010hidden}.
-Since the dialogue state is simplification of dialogue history and has no broadly-accepted form, it is very expensive to collect such annotated data because the dialogue state typically differs among domains and its structure is hard to explain to annotators.
-In this paper, we focus on collecting supervised training set with rich enough annotation so the supervised models similar to~\cite{wen2016network} can be trained with few hundreds of dialogues, but the annotation of dialogues are easier to collect.
+Current Spoken Dialogue Systems (SDS) are either handcrafted and use no training data~\cite{duvsek2014alex,raux2005let} but require non-trivial amount of expert work, or they are gradually improved from initial policy through live user interaction~\cite{young2010hidden,gasic2011line}.
+Recently, SDS have also been trained using supervised learning in an end-to-end manner~\cite{wen2016network,williams2016end}.\footnote{The~work of \cite{williams2016end} also fine-tuned the conversation with reinforcement learning after the supervised learning stage.}
+To train a system using reinforcement learning, one only needs to collect enough live user conversation containing explicit feedback.
+However, the feedback signal is harder to interpret than supervised annotation: Thousands of live conversations are required to improve a rather simple policy.\cite{gasic2011line}
+Supervised learning methods reduced the number of conversations needed for training a reasonable policy down to a few hundreds\cite{wen2016network}, but require explicit annotation for all components used in the dialogue system.
+To our knowledge, all current systems require full dialogue state annotation as a minimum~\cite{wen2016network,young2010hidden}.\OD{Tuhle větu asi do footnotu?}
+With the dialogue state being a simplification of the dialogue history with no broadly-accepted form, it is very expensive to collect such annotated data because the dialogue state typically differs among domains and its structure is hard to explain to annotators.
+In this paper, we focus on collecting a supervised training set with annotation rich enough so that supervised models similar to~\cite{wen2016network} can be trained with a few hundreds of dialogues, yet much easier to collect than previous methods.
 
-We believe that our dataset dataset can be used for first experiments of training end-to-end systems using supervised learning without annotated dialogue state.
-The domain of the dataset is well established thanks to dialogue state tracking (DST) challenges~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3}. 
-The DST challenges proved that the domain is of reasonable complexity.
+We believe that our dataset dataset can be used for first experiments in training end-to-end systems using supervised learning without explicit dialogue state annotation.
+The restaurant information domain used in our dataset is well established thanks to dialogue state tracking (DST) challenges~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3}. 
+The DST challenges proved that the domain is of a reasonable complexity.
 In addition, the challenges showed that the DST task is solvable by architectures which may be extended to end-to-end conversational agents~\cite{platek2016recurrent,vodolan2015hybrid,henderson2014word}.
-Note that we collected human-to-human dialogues on Cambridge restaurant domains, but our data-collection method is domain independent.
+Note that \ODdel{we collected human-to-human dialogues on Cambridge restaurant domains, but} our data-collection method is \OD{completely} domain independent.
 
-The paper is structured as follows: Section~\ref{sec:repre} motivates the annotations and format of our dataset.
-In Section~\ref{sec:collection} we introduce our collection process using crowdsourcing.
-Section~\ref{sec:props} presents the dataset properties and we list the related work in Section~\ref{sec:related}.
+The paper is structured as follows: Section~\ref{sec:repre} motivates the annotation and data formats\OD{?} used in our dataset.
+In Section~\ref{sec:collection}, we introduce our collection process using crowdsourcing.
+Section~\ref{sec:props} presents the dataset properties, and we list related work in Section~\ref{sec:related}.
 We conclude the paper and suggest future work in~Section~\ref{sec:conc}.
@@
 
-\section{Supervised feedback for task-oriented dialogue} \label{sec:repre}
+\section{Supervised Feedback for Task-oriented Dialogue} \label{sec:repre}
 \vspace{-0.50em}
@@
 \vspace{-0.50em}
-We just started to collect our dataset and so far we collected only 60 conversations.
+We just started to collect our dataset and so far we collected only \OP{62} conversations.
 The average length of a conversation is \OP{3.8} turns, meaning that the contributors in both roles reply in average circa three times before the conversation is finished\footnote{First system reply is automatically generated and for some conversation even the first client reply is also initialized as described in Section~\ref{sec:async}}.

### 2016-06-28 paper.tex
More stuff

@@
 \vspace{-0.50em}
-We present a dataset for training a task-oriented conversational agent in well defined domain.
-We assume that the agent has a task database\footnote{In the Cambridge restaurant domain the database is a simple table containing information about restaurants.} at hand and plays role of {\it operator}.
-The other interlocutor in the conversation is a~human {\it client}.
-{\it Clients} seek information stored in the database and use the system, which replaced a~human operator, to obtain desired information.
+We present a dataset for training a task-oriented conversational agent in a well-defined domain.\OD{In this paper, we assume that we need to train a...}
+We assume that the agent has a task database\footnote{In the Cambridge restaurant domain the database is a simple table containing information about restaurants.} at hand and plays the role of the {\it operator}.
+The other interlocutor in the conversation is a~human {\it client}.\OD{that seeks information stored in the database}
+Clients seek information stored in the database and use the system, which replaced a~human operator, to obtain desired information.\OD{A tuhle větu už pak můžeš vyhodit.}
 
 We focus on data collection for text-to-text task-oriented dialogue systems.
-Traditionally, one would train the pipeline of components of task-oriented dialogue systems, i.e.\ automatic speech recognition (ASR), language understanding (LU) unit, dialogue tracker (DT), dialogue manager (DM), natural language generator (NLG) for text-to-text conversational agents and text-to-speech (TTS) module~\cite{duvsek2014alex}.
-However, typically only the text-to-text pipeline of LU, DT, DM and NLG is trained using just the domain-related text-to-text data~\cite{gasic2011line,jurvcivcek2014factored,duvsek2016sequence}.
+Traditionally, one would train the pipeline of components of task-oriented dialogue systems, i.e., automatic speech recognition (ASR), language understanding (LU) unit, dialogue tracker (DT), dialogue manager (DM), natural language generator (NLG) for text-to-text conversational agents and text-to-speech (TTS) module~\cite{duvsek2014alex}.
+However, only the text-to-text pipeline of LU, DT, DM, and NLG is typically trained using just in-domain data~\cite{gasic2011line,jurvcivcek2014factored,duvsek2016sequence}.
 The ASR~\cite{platek2014free} and the TTS~\cite{taylor2009text} modules are typically trained using larger datasets.
-Our datasets contains data for training an~end-to-end system solving task of LU, DT, DM and NLG pipeline of traditional architecture.
+Our datasets contains data for training an~end-to-end system solving task of LU, DT, DM and NLG pipeline of traditional architecture.\OD{Tenhle odstavec bych ještě trochu překopal.}
 
@@
 % Zatim nechavam zde: \OD{následující dva odstavce zní dost jako “related work”... možná bych to tam částečně popřesouval? a tady nechal jen ten statement, že stačí málo trénovacích dat?}
-It was shown that few hundreds of annotated domain specific conversations is needed for training relatively well performing LU~\cite{jurvcivcek2014factored} as well as Dialogue State Tracking~\cite{young2010hidden} components.
-The work of~\cite{duvsek2016sequence} and~\cite{mairesse2010phrase} showed that only several hundreds of turns with appropriate annotation is needed for training usable NLG unit on simple domains.
-Even the crucial task of action selection can be trained using POMDP dialogue manager and few thousands conversations despite the fact that rewards are provided only at the end of dialogue~\cite{gasic2011line}.
+It was shown that a few hundreds of annotated domain specific conversations are needed to train a relatively well performing LU~\cite{jurvcivcek2014factored} as well as Dialogue State Tracking~\cite{young2010hidden} components.\OD{“few” = málo, “a few” = pár, několik}
+The work of~\cite{duvsek2016sequence} and~\cite{mairesse2010phrase} showed that only several hundreds of turns with appropriate annotation is needed for training a usable NLG unit in simple domains.
+Even the crucial task of action selection can be trained using a POMDP dialogue manager\OD{přepsal bych na “using reinforcement learning”, protože nikde nedefinuješ, co je POMDP} and few thousands conversations despite the fact that rewards are only provided at the end of a dialogue~\cite{gasic2011line}.
 
-We believe that end-to-end systems even can be trained using few hundreds conversation if additional supervision in the form of simple annotation is used for narrow goal-oriented domains such as Cambridge restaurant domain~\cite{henderson2014dstc2} or its simplification~\cite{wen2016network}.
-The~work of~\cite{wen2016network} showed that only 680 conversations annotated just at dialogue state level are needed for training the complete end-to-end system performing the task of summarizing the dialogue history, response planning and generation.
+We believe that end-to-end systems can also be trained using a few hundreds of conversations for narrow goal-oriented domains, such as Cambridge restaurant domain~\cite{henderson2014dstc2} or its simplification~\cite{wen2016network}, if additional supervision in the form of simple annotation is used.
+The~work of~\cite{wen2016network} showed that only 680 conversations annotated just at the dialogue state level are needed for training a complete end-to-end system performing the task of summarizing the dialogue history, action selection, and response generation.
 
-We realise that further annotation of dialogue conversation may help to train the models faster, but simply collecting more data is typically more beneficial.
-As a consequence, we see works~\cite{wen2016network,bordes2016learning,williams2016end} as important step forward to reducing the need of rich annotations for training dialogue agents.
-We believe that annotating a dialogue state according to expert-handcrafted ontology is both an~artificial and a~very labor-intensive data collection task, so our work aim at collecting conversation with lighter and more easier to get annotations.
-We suggest to record conversation between human operator and human clients through crowdsourcing and by this means collect cheap high quality training data.
-Similar recording setup is known from call centers where the operator is provided with interface to the database so it quickly finds relevant information and plays the role of domain expert.
-For our dataset, we collect the operator's database calls with its arguments instead of dialogue state annotation after each turn.
+We realize that a more fine-grained annotation helps to train the models faster, but simply collecting more data is often more beneficial.\OD{citace?
+a nevím, jestli tady ta věta je nutná.
+Možná bych vynechal všechno až do “we believe that annotating...”??}
+As a consequence, we regard the works~\cite{wen2016network,bordes2016learning,williams2016end} as an important step forward to reducing the need for rich annotation in dialogue agent training.
+We believe that annotating the dialogue state according to an expert-handcrafted ontology is both an~artificial and a~very labor-intensive data collection task.
+Therefore, our work aims at collecting conversation with lighter and easier to get annotation.
+We suggest recording conversation between a human operator and a human clients via a crowdsourcing platform, i.e., collecting cheap high quality training data.
+A similar recording setup is known from call centers where the operator is provided with a database interface so that they quickly find relevant information and play the role of a domain expert.
+For our dataset, we collect the operator's database calls instead of dialogue state annotation after each turn.\OD{Asi bych tohle dal hned po “eaiser to get annotation”.
+Pak tu větu “a similar recording setup...” a až na konec “we suggest crowdsourcing”, který bych změnil na “To obtain the dataset, we record conversations between human operators and human clients...”}
 
-The calls to the database completely represents the client intention which is the purpose of the dialogue state.
-On the other, the database calls are not present in every turn and thus by logging only the calls one loses a possibility to track partially filled client intention.
-We argue that in high quality human-human conversation there is a minimum turns which are related to the domain and do not contain calls to the database as demonstrated in~Section~\ref{sec:props}.
-It's worth noting that logging operator's database calls in operator-client dialogues is already well established practice in call centers, a~convenient field for commercial application of dialogue systems.
+The calls to the database represent very accurately the client's intention, which is the original purpose of dialogue state annotation.
+On the other hand, the database calls are not present in every turn and thus by logging only the calls, one loses the possibility to track partially expressed client's intention.
+However, we argue that in high quality human-human conversation, there are few turns which are related to the domain and do not contain calls to the database, as demonstrated in~Section~\ref{sec:props}.
+It is worth noting that logging the operator's database calls in operator-client dialogues is already a well-established practice in call centers, a~convenient field for commercial application of dialogue systems.
 
@@
 \vspace{-0.50em}
-Our data collection processed aimed at collecting natural conversation in the well defined domain.
-We decided to collect new dataset int the~well studied Cambridge restaurant domain since the previous datasets~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3} in that domain demonstrated that a meaningful and of a reasonable length conversation can be held in the domain.
-Also it was proven that the domain is on one hand difficult enough that even the state-of-the art systems does not reach human-level performance in the role of the operator~\cite{henderson2014dstc2} and on the other hand numerous systems~\cite{young2010hidden,gasic2011line,wen2016network} demonstrated that are able to provide information to the clients reasonable well.
+Our data collection process aims at obtaining natural in-domain conversations.
+We decided to collect the dataset within the~well studied Cambridge restaurant domain since previous datasets~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3} in that domain demonstrated that a meaningful and reasonable-length conversations can be held here.\OD{tady už se částečně opakuješ, na jednom místě to zkrať}
+Also, it was proven that the domain is on one hand difficult enough that even the state-of-the art systems do not reach human-level performance in the role of the operator~\cite{henderson2014dstc2} and on the other hand, numerous systems~\cite{young2010hidden,gasic2011line,wen2016network} demonstrated their ability to provide information to the clients with a reasonable quality.
 
-We define our domain by choosing a database from Dialogue State Tracking Challenge 2 (DSTC2)~\cite{henderson2014dstc2}.
-We use the database for steering the dialogue of the two human interlocutors a~{\it client} and an~{\it operator}.
-We use the CrowdFlower (CF) crowdsourcing platform for collecting the conversations.
+We define our domain by choosing the database from the 2nd Dialogue State Tracking Challenge (DSTC2)~\cite{henderson2014dstc2}.
+We use the database for steering the dialogue of the two human interlocutors a~{\it client} and an~{\it operator}.\OD{tuhle větu bych vynechal}
+We use the CrowdFlower (CF) crowdsourcing platform to collect the conversations.
 
 We first describe the database which defines our domain in~Section~\ref{sec:db}.
-Then we describe how the hired workers used our interface for playing either client or operator roles in~Sections~\ref{sec:client} and~\ref{sec:operator}.
-Finally, in~Section~\ref{sec:async} we describe how we collected conversations one response at a time without connecting the interlocutors in real-time.
+Then we describe how the hired workers use our interface to play either the client or the operator role in~Sections~\ref{sec:client} and~\ref{sec:operator}, respectively.
+Finally, in~Section~\ref{sec:async}, we describe how we collect conversations one response at a time without connecting the interlocutors in real-time.
 
@@
 
-We used exactly the same database as provided for the DSTC2 challenge~\cite{henderson2014dstc2}.
-The database contains information about 107 restaurants and their properties stored in the columns.
+We use exactly the same database as provided for the DSTC2 challenge~\cite{henderson2014dstc2}.
+The database contains information about 107 restaurants in Cambridge, and their properties are stored in several columns.
 We include in brackets the number of different values for each column:
-\vspace{-0.50em}
+\vspace{-0.50em}\OD{Když dáš dvousloupcovou tabulku, tak i ušetříš trochu místa}
 \begin{itemize}  % tabulku misto tohohle?
@@
     \item address (101),
-    \item phone (97),
+    \item phone number (97),
     \item postcode (62).
@@
 
-The address or the phone are unique for each restaurant but are sometimes missing, but the name of the restaurant is always known. 
-There are typically multiple restaurant with the same postcode, price range, area, or food type property and these properties might be unknown for a restaurant.
+The address and the phone number are unique for each restaurant but are sometimes missing; the restaurant name is always known. 
+There are typically multiple restaurants with the same postcode, price range, area, or food type properties; these properties might also be unknown for a restaurant.
 
-We use the database to generate client goals for CF users (see Figure~\ref{fig:client}).
-The database was also available to CF users playing role of the operator through a simple interface (see Figure~\ref{fig:operator}).
+We use this database to generate\OD{prepare} client goals for CF users (see Figure~\ref{fig:client}).
+The database is also available through a simple interface to CF users playing the role of the operator (see Figure~\ref{fig:operator}).\OD{nechceš tu odkazovat na ty podsekce spíš než na ty obrázky?}
 
@@
 
-The client is asked to request a specific information - a goal from the operator.
+The client is asked to request a specific information – a goal from the operator.
 He may choose not to seek the goal immediately but submit more appropriate response such as greeting instead.

### 2016-06-28 paper.tex
Attempt to straighten the diffs

@@
 We present a new dataset of human-human task-oriented conversations in the restaurant information domain, suitable for supervised training of autonomous systems. 
-Currently, the dataset contains only \OP{62} dialogues because we are still collecting more data, but we estimate we will have more than 700 dialogues until the camera ready deadline.
-\OD{We are currently collecting data for the set using crowdsourcing.
+Currently, the dataset contains only \OP{62} dialogues because we are still collecting more data, but we estimate we will have more than 700 dialogues until the camera ready deadline.\OD{We are currently collecting data for the set using crowdsourcing.
 We have collected 62 dialogues so far; more than 700 dialogues are planned for the final version of the dataset.\footnote{\OD{We expect to release the set before the camera-ready deadline.}}}

### 2016-06-28 paper.tex
Sect 3

@@
 \vspace{-1.00em}
-\subsection{Domain database}
+\subsection{Domain Database}
 \label{sec:db}
@@
 \vspace{-1.00em}
-\subsection{Client interface}
+\subsection{Client Interface}
 \label{sec:client}
 
-The client is asked to request a specific information – a goal from the operator.
-He may choose not to seek the goal immediately but submit more appropriate response such as greeting instead.
-The goals are displayed to the CF worker in the client role gradually turn-by-turn and the goals may contradict each other.
-For example, the client may at first want a Chinese food, but later it changes her mind and wants to find restaurant serving British food.
+The CF worker playng the role of the client is asked to request specific information from the operator – a goal.
+They may choose not to seek the goal immediately but submit more appropriate response such as greeting instead.
+The goals are displayed to the CF worker in the client role gradually turn-by-turn and may contradict each other.
+For example, the client may at first want a to find a restaurant serving Chinese food, but later change their mind and seek British food.
 
-Before submitting a reply the client is instructed to read the dialogue history and marked the goals which were presented to the operator as demonstrated in Figure~\ref{fig:client}.
-By marking which goals have been already presented to the operator we force the CF workers to pay attention to the dialogue history before submitting their reply.
-In Section~\ref{sec:async} we describe how we combine the workers replies to form a~conversations.
+Before submitting a reply, the client is instructed to read the dialogue history and mark the goals which were already presented to the operator, as demonstrated in Figure~\ref{fig:client}.\OD{teď nevím, jestli “goal” je celkový cíl, nebo jestli jich má ten worker víc -- to by bylo potřeba jednotně.}
+By marking which goals have already been presented to the operator, we force\OD{oblige?} the CF workers to pay attention to the dialogue history before submitting their reply.\OD{do footnotu explicitně vysvětlit, proč to tak je -- proč nemůžou klikat náhodně (že další user vlastně kontroluje toho předchozího tím, že musí zaškrtnout nadmnožinu dříve zaškrtnutých cílů)?}
+In Section~\ref{sec:async}, we describe how we combine the workers' replies to form a conversation.\OD{tuhle větu na začátek sekce?}
 
-\begin{figure}
+\begin{figure}[tb] % ať se nemrhá místem
 \vspace{-1.00em}
@@
 \vspace{-1.00em}
-\subsection{Operator interface}
+\subsection{Operator Interface}
 \label{sec:operator}
-The operator is asked to politely reply the clients needs according the information stored in the database.
-In order to provide the information to clients the operator uses the DB interface depicted in~Figure~\ref{fig:operator}.
-Her or she filters the restaurants using a full text search on the database.
-The content of the database is intentional hidden if no filter is specified so the filter has to be used.
-The CF workers are also instructed explicitly mark the rows of the restaurants about which provide the information in their answer.
-Similarly to the client role, an operator does not have to reply to all requested information at once.
-It is up to the~worker which information is provided first.
+The operator CF worker is asked to politely address the clients needs according to the information stored in the database.
+In order to provide the information to clients, the operator uses the simple database interface depicted in~Figure~\ref{fig:operator}:
+They filter the restaurants using a full text search over the database.
+The content of the database is intentionally hidden if no filter is specified so that a filter has to be used to provide results.
+The CF workers are also instructed to explicitly mark the database rows to which they refer in their answer.
+Similarly to the client role, the operator does not have to provide all requested information in a single turn.
+It is left up to the~worker which information is provided first.
 
-The full text search, our interface to the database, is implemented in Javascript as a simple substring matching over values in the database.
+Our full text search interface to the database is implemented in Javascript as a simple substring matching over values in the database.
 Multiple constrains can be expressed by two substrings separated by a comma.
-We used such a simple interface because it is easy to generate and also reconstruct the candidate results given the query and the database.
-The CF workers were instructed to mark a candidate row from the results about which they inform in their reply.
+We used such a simple interface because it is easy to generate and also reconstruct the candidate results given the query and the database.\OD{co znamená “easy to generate”?
+hlavně taky “easy to use for untrained CF workers”, to mi přijde důležitější, ne?
+možná bych ty detaily o tom interfacu hodil rovnou za “using a full text search over the database”}
+\ODdel{The CF workers were instructed to mark a candidate row from the results about which they inform in their reply.}\OD{tady se opakuješ}
 
-\begin{figure}
+\begin{figure}[tb]
 \vspace{-1.00em}
@@
 \label{sec:async}
-We design the crowdsourcing jobs so the CF contributors are able to work independently to each other.
-The roles of client and operator take turns as sets of partial conversations are submitted for collecting a single new response.
+We design the crowdsourcing jobs so that the CF contributors are able to work independently of each other.
+The roles of client and operator take turns as partial conversations are submitted to CF for collecting a single new response.\OD{přijde mi, že “sets of” to spíš zamlží}
 As a consequence, a~single conversation is collected from multiple contributors over several job submissions.
 
-Each utterance in conversation may be submitted by different contributor, so contributors need to read carefully the dialogue history to understand the conversation before submitting their response.
-The workers are able to mark dialogues which does not make sense and thus they self-assess quality of the conversations.
-The contributors mark the conversations as finished if they have no more goals to fulfill and all the goodbyes were said.
+Each utterance in the conversation may be submitted by a different contributor.
+Therefore, the contributors need to read carefully the dialogue history to understand the conversation before submitting their response.
+The workers are able to mark dialogues which do not make sense and thus they self-assess the quality of the conversations.
+The contributors mark the conversations as finished if they have no more goals to fulfill and all the goodbyes have been said.
 
-We bootstrap the conversation either with an operators introduction "{\it Hello , welcome to the Cambridge restaurant system...}" or we bootstrap the conversation with a~full turn where we add clients greeting e.g.
-{\it "Hi"} to aforementioned operators utterance.
-If we initialize the dialogue with a~full turn the first contributor plays role of the system if we bootstrap the conversation only with~the operators greeting, the contributor plays the client's role.
+We bootstrap the conversation either with an operator's introduction {\it ``Hello , welcome to the Cambridge restaurant system...''}, or we bootstrap the conversation with a~full turn where we add a client's greeting, e.g., {\it ``Hi''} to the operator's introduction.
+If we initialize the dialogue with a~full turn, the first contributor plays role of the system.
+If we bootstrap the conversation only with~the operator's greeting, the first contributor plays the client's role.
 
-In a~single job submission, we let the workers append to each dialogue a~single response.
-Note also that the conversations are typically rather short so full dialogues are collected after few rounds of submissions.
-The workers are paid for every submitted response the same amount independently if they play client or operator role and they typically contribute to multiple conversation during one job submission.
-The contributors are assigned roles randomly.
+In a~single CF task submission, we let the workers append a~single response to multiple different dialogues, taking on a random role in each of them.
+That the conversations are typically rather short \OD{možná rekni počet turnů, ať to nevypadá jako dva} and therefore, full dialogues are collected after few rounds of submissions.
+The workers are paid  the same amount of money for every submitted response regardless of whether they play the client or the operator role.
+\ODdel{and they typically contribute to multiple conversation during one job submission.}\OD{přidal jsem do první věty)}
+\ODdel{The contributors are assigned roles randomly.}\OD{ditto}
 
-To avoid poor language level of English we restricted the CF worker to English-speaking countries.
-We further perform heuristically check for too trivial answers and we added ability to the CF workers to rate each others submission.
-It help us filter low quality conversations, but more importantly it motivated workers not to cheat.
+To avoid poor language level of English, we restricted the CF job to English-speaking countries.
+We further perform heuristic checks for too trivial replies, and we enable the CF workers to rate each other's responses.
+This help us filter low-quality conversations, but more importantly, it motivates the CF workers not to cheat.
 

### 2016-06-28 paper.tex
The rest

@@
 In a~single CF task submission, we let the workers append a~single response to multiple different dialogues, taking on a random role in each of them.
-That the conversations are typically rather short \OD{možná rekni počet turnů, ať to nevypadá jako dva} and therefore, full dialogues are collected after few rounds of submissions.
+The conversations are typically rather short \OD{možná rekni počet turnů, ať to nevypadá jako dva} and therefore, full dialogues are collected after few rounds of submissions.
 The workers are paid  the same amount of money for every submitted response regardless of whether they play the client or the operator role.
@@
 \vspace{-0.50em}
-We just started to collect our dataset and so far we collected only \OP{62} conversations.
-The average length of a conversation is \OP{3.8} turns, meaning that the contributors in both roles reply in average circa three times before the conversation is finished\footnote{First system reply is automatically generated and for some conversation even the first client reply is also initialized as described in Section~\ref{sec:async}}.
-During an average conversation \OP{2.4} tasks are requested and \OP{1.9} answered.
+We just started to collect our dataset and so far, we have only collected \OP{62} conversations.
+The average length of a conversation is \OP{3.8} turns, meaning that the contributors in both roles reply in average circa three times before the conversation is finished\footnote{The first system utterance is automatically generated and for some conversations, the first client reply is also generated automatically, as described in Section~\ref{sec:async}}.
+During an average conversation, \OP{2.4} tasks are requested and \OP{1.9} answered.\OD{Proč ne všechny? To by možná bylo dobrý vysvětlit}
 % Typically in \OP{65} \% case the conversation is ended by the client.
@@
 % \end{table}
-During the data collection process we discarded over \OP{35} \% of replies because the utterances were of low quality.
-Note that we discard only the low quality utterance, the prefix of the conversation is submitted for finishing the conversation in next rounds of jobs.
-Once we will collect enough conversation we intend to split them into training, development and test set. % (see Table~\ref{tab:props}).
+During the data collection process we discarded around \OP{35} \% of replies so far because the utterances were of low quality.
+Note that we discard only the low-quality utterance; the prefix of the conversation is submitted for finishing the conversation in a next round of CF tasks.
+Once we collect enough conversations, we intend to split them into training, development and test set. % (see Table~\ref{tab:props}).
 
@@
 Our work is closely related  to work of~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3} in the sense that the conversation are held in the same domain.
-On the other hand, the collection process differs substantially because we do not use any artificial system in the operator's role.  
-We rather focus on collecting high quality human conversations. 
-In addition, in our work we do not collect complicated annotations on LU and DST level.
+On the other hand, the collection process differs substantially because we do not use any artificial system in the operator's role;
+we rather focus on collecting high-quality human-human conversations. 
+In addition, we do not collect complex LU and DST annotation in our work.
 
-A~relevant work of~\cite{wen2016network} collected human-human dialogues in similar but more restricted domain than the Cambridge domain.
-Their dataset is not yet published so we compare only with their statistics.
-The dataset is of similar size as we intend to collect and a~very similar collection scheme was used where Amazon Mechanical Turk workers submitted one reply at a time without being connected to each other in real-time.
-On the other hand, they collected explicit dialogue state annotation which takes significant annotation effort.
+The~relevant work of~\cite{wen2016network} includes a collection of human-human dialogues in a domain similar to ours but more restricted.
+Their dataset is not yet publicly available; therefore, we only compare to their statistics.
+The dataset is of similar size as we intend to collect, and a~very similar collection scheme was used where Amazon Mechanical Turk workers submitted one reply at a time without being connected to each other in real-time.
+On the other hand, they collected explicit dialogue state annotation, which takes a significant annotation effort.
 
-Another line of research~\cite{vodolan2016data} used CF to collect human-human conversation for interactive-learning dataset.
-However, the collected dialogues were later annotated by expert annotators which goes directly against our intentions to avoid any expensive annotations.
+Another line of research~\cite{vodolan2016data} used CF to collect human-human conversations for interactive learning dataset.
+However, the collected dialogues were later annotated by expert annotators, which goes directly against our intentions to avoid any expensive annotation.
 
-There is a~significant amount of work which used Wizard of Oz experiments~\cite{whittaker2002fish,walker1997evaluating,rieser2008learning} for studying linguistic properties of dialogues, evaluating proof of concept or even collecting bootstrap training data, but according our knowledge no other work than~\cite{wen2016network} have used cheap crowdsourcing workers to collect a~full training dataset for supervised learning of dialogue management or end-to-end conversations.
+There is a~significant amount of work which used Wizard-of-Oz experiments~\cite{whittaker2002fish,walker1997evaluating,rieser2008learning} for studying linguistic properties of dialogues, evaluating proof-of-concept\OD{proof of concept čeho??} or even collecting bootstrap training data but to our knowledge, no other work than~\cite{wen2016network} have used cheap crowdsourcing workers to collect a~full training dataset for supervised learning of dialogue management or end-to-end conversations.
 
@@
 \vspace{-0.50em}
-We present a new human-human dialogue dataset with annotation of user intention in form of operator's database calls.
-We also introduced a novel data collection setting which resembles work of operators in call centers and introduce minimum overhead to crowdsourcing workers.
+We present a new human-human dialogue dataset with annotation of user intention in the form of operator's database calls.
+We also introduced a novel data collection setting which resembles work of operators in call centers and introduces minimum overhead to crowdsourcing workers.
 % TO mi prijde ze v call -centrech delaji stejne\OD{, apart from stating their replies in natural language (?)}
-The collected dialogues are published under Creative Commons 4.0 BY-SA license on available to download at {\it anonymized}.  % lindat\footnote{todo where}.
+The collected dialogues are published under Creative Commons 4.0 BY-SA license and available for download \ODdel{at {\it anonymized}}.\OD{Napsal bych radši do footnotu “URL will be provided in the camera-ready version of the paper”).}  % lindat\footnote{todo where}.
 
-We plan to increase the number of collected dialogues till the camera ready deadline to 700 or more.
-We intend to use the dataset to train and evaluate an~end-to-end conversational model which uses only the database calls as additional supervision to the recorded responses.
+We plan to increase the number of collected dialogues to 700 or more before the camera-ready deadline.
+We intend to use the dataset to train and evaluate an~end-to-end conversational model which uses only operator's database calls as additional supervision to the recorded responses.
 
@@
 We would like to thank Ondřej Dušek for useful comments.
-This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333.
+This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333.\OD{Pro anonymizaci tuhle sekci zatím vynech.
+V plné verzi bys měl asi poděkovat i Lindatu.}
 % We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.

### 2016-06-28 paper.tex
od changes and rewrote the worst paragraph

@@
 
-\title{A Dataset of Operator-client Dialogues Aligned with Database Queries}
+\title{A Dataset of Operator-client Dialogues Aligned with Database Queries for End-to-end training}
 
@@
 % \OP{grammar check} \\
-\OD{Přemýšlím, jestli ten název neudělat nějak míň popisný a víc vysvětlující (něco o end-to-end dialogue systems)?}
 
@@
 We present a new dataset of human-human task-oriented conversations in the restaurant information domain, suitable for supervised training of autonomous systems. 
-Currently, the dataset contains only \OP{62} dialogues because we are still collecting more data, but we estimate we will have more than 700 dialogues until the camera ready deadline.\OD{We are currently collecting data for the set using crowdsourcing.
-We have collected 62 dialogues so far; more than 700 dialogues are planned for the final version of the dataset.\footnote{\OD{We expect to release the set before the camera-ready deadline.}}}
+We are currently collecting data for the set using crowdsourcing.
+We have collected 62 dialogues so far; more than 700 dialogues are planned for the final version of the dataset.\footnote{We expect to release the set before the camera-ready deadline.}
 
 We aim at representing the conversation in a way that makes it easy to train an automated system to replace a human operator. 
-In contrast to previously released datasets, our dataset contains easy-to-collect high-quality transcriptions of the client and operator actions during conversations.\OD{tady úplně nevím, k čemu se kontrastuješ}
+Our dataset contains easy-to-collect high-quality transcriptions of the client and operator actions during conversations.
 We introduce a~very little overhead by collecting database calls in addition to the transcription of the conversation.
 In fact, we mimic very closely a~real situation in call centers where operators search for answers through a database user interface. 
-Just logging the calls to the task database provide us with information of a similar quality as a full manual dialogue state annotation, but not annotated incrementally after each turn.\OD{od “but” nerozumím}
-Tracking the database calls in task oriented systems together with conversation transcription should not introduce significant overhead during the data collection, but should presumably boost end-to-end conversational agent as much as annotated dialogue state when training with such data.\OD{but should provide a similar amount of supervision for training an end-to-end conversational agent as using fully annotated dialogue state ??}
+Just logging the calls to the task database provide us with information of a similar quality as a full manual dialogue state annotation.
+Tracking the database calls in task oriented systems together with conversation transcription should not introduce significant overhead during the data collection, but should provide a similar amount of supervision for training an end-to-end conversational agent as using fully annotated dialogue state.
 
@@
 However, the feedback signal is harder to interpret than supervised annotation: Thousands of live conversations are required to improve a rather simple policy.\cite{gasic2011line}
-Supervised learning methods reduced the number of conversations needed for training a reasonable policy down to a few hundreds\cite{wen2016network}, but require explicit annotation for all components used in the dialogue system.
-To our knowledge, all current systems require full dialogue state annotation as a minimum~\cite{wen2016network,young2010hidden}.\OD{Tuhle větu asi do footnotu?}
+Supervised learning methods reduced the number of conversations needed for training a reasonable policy down to a few hundreds\cite{wen2016network}, but require explicit annotation for all components used in the dialogue system.\footnote{To our knowledge, all current systems require full dialogue state annotation as a minimum~\cite{wen2016network,young2010hidden}.}
 With the dialogue state being a simplification of the dialogue history with no broadly-accepted form, it is very expensive to collect such annotated data because the dialogue state typically differs among domains and its structure is hard to explain to annotators.
@@
 In addition, the challenges showed that the DST task is solvable by architectures which may be extended to end-to-end conversational agents~\cite{platek2016recurrent,vodolan2015hybrid,henderson2014word}.
-Note that \ODdel{we collected human-to-human dialogues on Cambridge restaurant domains, but} our data-collection method is \OD{completely} domain independent.
+Note that our data-collection method is completely domain independent.
 
-The paper is structured as follows: Section~\ref{sec:repre} motivates the annotation and data formats\OD{?} used in our dataset.
+The paper is structured as follows: Section~\ref{sec:repre} motivates the annotations and collection procedure used in our dataset.
 In Section~\ref{sec:collection}, we introduce our collection process using crowdsourcing.
@@
 \vspace{-0.50em}
-We present a dataset for training a task-oriented conversational agent in a well-defined domain.\OD{In this paper, we assume that we need to train a...}
-We assume that the agent has a task database\footnote{In the Cambridge restaurant domain the database is a simple table containing information about restaurants.} at hand and plays the role of the {\it operator}.
-The other interlocutor in the conversation is a~human {\it client}.\OD{that seeks information stored in the database}
-Clients seek information stored in the database and use the system, which replaced a~human operator, to obtain desired information.\OD{A tuhle větu už pak můžeš vyhodit.}
+In this paper, we assume that we need to train a~task-oriented conversational agent in a well-defined domain.
+We suppose that the agent has a task database\footnote{In the Cambridge restaurant domain the database is a simple table containing information about restaurants.} at hand and plays the role of the {\it operator}.
+The other interlocutor in the conversation is a~human {\it client} that seeks information stored in the database.
 
-We focus on data collection for text-to-text task-oriented dialogue systems.
-Traditionally, one would train the pipeline of components of task-oriented dialogue systems, i.e., automatic speech recognition (ASR), language understanding (LU) unit, dialogue tracker (DT), dialogue manager (DM), natural language generator (NLG) for text-to-text conversational agents and text-to-speech (TTS) module~\cite{duvsek2014alex}.
-However, only the text-to-text pipeline of LU, DT, DM, and NLG is typically trained using just in-domain data~\cite{gasic2011line,jurvcivcek2014factored,duvsek2016sequence}.
-The ASR~\cite{platek2014free} and the TTS~\cite{taylor2009text} modules are typically trained using larger datasets.
-Our datasets contains data for training an~end-to-end system solving task of LU, DT, DM and NLG pipeline of traditional architecture.\OD{Tenhle odstavec bych ještě trochu překopal.}
+The task of building a conversational agents is traditionally simplified by creating pipeline of subtasks: each solved by specialised components: automatic speech recognition (ASR), language understanding (LU) unit, dialogue tracker (DT), dialogue manager (DM), natural language generator (NLG) and text-to-speech (TTS) module~\cite{duvsek2014alex}.
+The ASR~\cite{platek2014free} and TTS~\cite{taylor2009text} modules can be easily trained from data without understanding the meaning of the data and there are typically domain independent.
+The crucial task of conversation agents is to understand the dialogue history and respond with a reply which has the greatest expected benefit for the agent.
+The task of understanding and reply generation is traditionally solved by the text-to-text pipeline of LU, DT, DM, and NLG trained using just in-domain data~\cite{gasic2011line,jurvcivcek2014factored,duvsek2016sequence} annotated at level of each component.
+Our datasets provides just the textual input-output transcriptions of in~domain conversations and simple annotations in form of database calls.
+We expect that supervised models will be able model the meaning of the history and select its reply only from the transcriptions and the annotation.
 
@@
 % Zatim nechavam zde: \OD{následující dva odstavce zní dost jako “related work”... možná bych to tam částečně popřesouval? a tady nechal jen ten statement, že stačí málo trénovacích dat?}
-It was shown that a few hundreds of annotated domain specific conversations are needed to train a relatively well performing LU~\cite{jurvcivcek2014factored} as well as Dialogue State Tracking~\cite{young2010hidden} components.\OD{“few” = málo, “a few” = pár, několik}
+It was shown that a few hundreds of annotated domain specific conversations are needed to train a relatively well performing LU~\cite{jurvcivcek2014factored} as well as Dialogue State Tracking~\cite{young2010hidden} components.
 The work of~\cite{duvsek2016sequence} and~\cite{mairesse2010phrase} showed that only several hundreds of turns with appropriate annotation is needed for training a usable NLG unit in simple domains.
-Even the crucial task of action selection can be trained using a POMDP dialogue manager\OD{přepsal bych na “using reinforcement learning”, protože nikde nedefinuješ, co je POMDP} and few thousands conversations despite the fact that rewards are only provided at the end of a dialogue~\cite{gasic2011line}.
+Even the crucial task of action selection can be trained using a reinforcement learning dialogue manager and few thousands conversations despite the fact that rewards are only provided at the end of a dialogue~\cite{gasic2011line}.
 
@@
 
-We realize that a more fine-grained annotation helps to train the models faster, but simply collecting more data is often more beneficial.\OD{citace?
+% We realize that a more fine-grained annotation helps to train the models faster, but simply collecting more data is often more beneficial.\OD{citace?
 a nevím, jestli tady ta věta je nutná.
 Možná bych vynechal všechno až do “we believe that annotating...”??}
-As a consequence, we regard the works~\cite{wen2016network,bordes2016learning,williams2016end} as an important step forward to reducing the need for rich annotation in dialogue agent training.
-We believe that annotating the dialogue state according to an expert-handcrafted ontology is both an~artificial and a~very labor-intensive data collection task.
-Therefore, our work aims at collecting conversation with lighter and easier to get annotation.
-We suggest recording conversation between a human operator and a human clients via a crowdsourcing platform, i.e., collecting cheap high quality training data.
+% As a consequence, we regard the works~\cite{wen2016network,bordes2016learning,williams2016end} as an important step forward to reducing the need for rich annotation in dialogue agent training.
+We realize that annotating the dialogue state according to an expert-handcrafted ontology is both an~artificial and a~very labor-intensive data collection task. 
+Therefore, our work aims at collecting conversation with lighter and easier to get annotations.
+For our dataset, we collect the operator's database calls instead of dialogue state annotation after each turn
 A similar recording setup is known from call centers where the operator is provided with a database interface so that they quickly find relevant information and play the role of a domain expert.
-For our dataset, we collect the operator's database calls instead of dialogue state annotation after each turn.\OD{Asi bych tohle dal hned po “eaiser to get annotation”.
+To obtain the dataset, we record conversations between a human operator and a human clients via a crowdsourcing platform, i.e., collecting cheap high quality training data.
+% OP the previous version and this much better OD version - what is the pattern here?.\OD{Asi bych tohle dal hned po “eaiser to get annotation”.
 Pak tu větu “a similar recording setup...” a až na konec “we suggest crowdsourcing”, který bych změnil na “To obtain the dataset, we record conversations between human operators and human clients...”}
@@
 Our data collection process aims at obtaining natural in-domain conversations.
-We decided to collect the dataset within the~well studied Cambridge restaurant domain since previous datasets~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3} in that domain demonstrated that a meaningful and reasonable-length conversations can be held here.\OD{tady už se částečně opakuješ, na jednom místě to zkrať}
+We selected the restaurant domain because it is convenient for collecting shorter, several turns-long conversations.
 Also, it was proven that the domain is on one hand difficult enough that even the state-of-the art systems do not reach human-level performance in the role of the operator~\cite{henderson2014dstc2} and on the other hand, numerous systems~\cite{young2010hidden,gasic2011line,wen2016network} demonstrated their ability to provide information to the clients with a reasonable quality.
-
 We define our domain by choosing the database from the 2nd Dialogue State Tracking Challenge (DSTC2)~\cite{henderson2014dstc2}.
-We use the database for steering the dialogue of the two human interlocutors a~{\it client} and an~{\it operator}.\OD{tuhle větu bych vynechal}
 We use the CrowdFlower (CF) crowdsourcing platform to collect the conversations.
@@
 We include in brackets the number of different values for each column:
-\vspace{-0.50em}\OD{Když dáš dvousloupcovou tabulku, tak i ušetříš trochu místa}
+% \OD{Když dáš dvousloupcovou tabulku, tak i ušetříš trochu místa}
+\vspace{-0.50em}
 \begin{itemize}  % tabulku misto tohohle?
@@
 
-We use this database to generate\OD{prepare} client goals for CF users (see Figure~\ref{fig:client}).
-The database is also available through a simple interface to CF users playing the role of the operator (see Figure~\ref{fig:operator}).\OD{nechceš tu odkazovat na ty podsekce spíš než na ty obrázky?}
+We use this database to prepare client goals for CF users (see Section~\ref{sec:client}).
+The database is also available through a simple interface to CF users playing the role of the operator (see Section~\ref{sec:operator}).
 
@@
 
-The CF worker playng the role of the client is asked to request specific information from the operator – a goal.
+The CF worker playing the role of the client is asked to request specific information from the operator – a goal.
 They may choose not to seek the goal immediately but submit more appropriate response such as greeting instead.
@@
 
-Before submitting a reply, the client is instructed to read the dialogue history and mark the goals which were already presented to the operator, as demonstrated in Figure~\ref{fig:client}.\OD{teď nevím, jestli “goal” je celkový cíl, nebo jestli jich má ten worker víc -- to by bylo potřeba jednotně.}
-By marking which goals have already been presented to the operator, we force\OD{oblige?} the CF workers to pay attention to the dialogue history before submitting their reply.\OD{do footnotu explicitně vysvětlit, proč to tak je -- proč nemůžou klikat náhodně (že další user vlastně kontroluje toho předchozího tím, že musí zaškrtnout nadmnožinu dříve zaškrtnutých cílů)?}
-In Section~\ref{sec:async}, we describe how we combine the workers' replies to form a conversation.\OD{tuhle větu na začátek sekce?}
+Before submitting a reply, the client is instructed to read the dialogue history and mark the goals which were already presented to the operator, as demonstrated in Figure~\ref{fig:client}.
+By marking which goals have already been presented to the operator, we oblige the CF workers to pay attention to the dialogue history before submitting their reply.
+% TODO - podmnozinovy check neni naimplementovan a asi by opravdu mel byt \OD{do footnotu explicitně vysvětlit, proč to tak je -- proč nemůžou klikat náhodně (že další user vlastně kontroluje toho předchozího tím, že musí zaškrtnout nadmnožinu dříve zaškrtnutých cílů)?}
 
@@
 They filter the restaurants using a full text search over the database.
+The~search interface is implemented in Javascript as a simple substring matching over values in the database.
+We used such a simple interface because it is easy use for untrained CF workers.
+Multiple constrains can be expressed by two substrings separated by a comma.
 The content of the database is intentionally hidden if no filter is specified so that a filter has to be used to provide results.
@@
 It is left up to the~worker which information is provided first.
-
-Our full text search interface to the database is implemented in Javascript as a simple substring matching over values in the database.
-Multiple constrains can be expressed by two substrings separated by a comma.
-We used such a simple interface because it is easy to generate and also reconstruct the candidate results given the query and the database.\OD{co znamená “easy to generate”?
-hlavně taky “easy to use for untrained CF workers”, to mi přijde důležitější, ne?
-možná bych ty detaily o tom interfacu hodil rovnou za “using a full text search over the database”}
-\ODdel{The CF workers were instructed to mark a candidate row from the results about which they inform in their reply.}\OD{tady se opakuješ}
 
@@
 \label{sec:async}
+In this section, we describe how we combine the workers' replies to form a conversation.
 We design the crowdsourcing jobs so that the CF contributors are able to work independently of each other.
-The roles of client and operator take turns as partial conversations are submitted to CF for collecting a single new response.\OD{přijde mi, že “sets of” to spíš zamlží}
+The roles of client and operator take turns as partial conversations are submitted to CF for collecting a single new response.
 As a consequence, a~single conversation is collected from multiple contributors over several job submissions.
@@
 In a~single CF task submission, we let the workers append a~single response to multiple different dialogues, taking on a random role in each of them.
-The conversations are typically rather short \OD{možná rekni počet turnů, ať to nevypadá jako dva} and therefore, full dialogues are collected after few rounds of submissions.
+The conversations are typically rather short circa four turns and therefore, full dialogues are collected after few rounds of submissions.
 The workers are paid  the same amount of money for every submitted response regardless of whether they play the client or the operator role.
-\ODdel{and they typically contribute to multiple conversation during one job submission.}\OD{přidal jsem do první věty)}
-\ODdel{The contributors are assigned roles randomly.}\OD{ditto}
 
@@
 The average length of a conversation is \OP{3.8} turns, meaning that the contributors in both roles reply in average circa three times before the conversation is finished\footnote{The first system utterance is automatically generated and for some conversations, the first client reply is also generated automatically, as described in Section~\ref{sec:async}}.
-During an average conversation, \OP{2.4} tasks are requested and \OP{1.9} answered.\OD{Proč ne všechny? To by možná bylo dobrý vysvětlit}
+During an average conversation, \OP{2.4} goals are requested and \OP{1.9} answered.
+There are two reason why there is more goals requested than answered.
+We saw a rare case when the goal was actually answered, but was not left marked as unanswered.
+However, much more common case is that the client asks for several goals e.g. phone and address, but he is satisfied if the operator provides just one of the goals e.g. phone. 
 % Typically in \OP{65} \% case the conversation is ended by the client.
@@
 
-There is a~significant amount of work which used Wizard-of-Oz experiments~\cite{whittaker2002fish,walker1997evaluating,rieser2008learning} for studying linguistic properties of dialogues, evaluating proof-of-concept\OD{proof of concept čeho??} or even collecting bootstrap training data but to our knowledge, no other work than~\cite{wen2016network} have used cheap crowdsourcing workers to collect a~full training dataset for supervised learning of dialogue management or end-to-end conversations.
+There is a~significant amount of work which used Wizard-of-Oz experiments~\cite{whittaker2002fish,walker1997evaluating,rieser2008learning} for studying linguistic properties of dialogues, evaluating proof-of-concept of a~dialogue system or even collecting bootstrap training data.
+However, to our knowledge, no other work than~\cite{wen2016network} have used cheap crowdsourcing workers to collect a~full training dataset for supervised learning of dialogue management or end-to-end conversations.
 
@@
 We also introduced a novel data collection setting which resembles work of operators in call centers and introduces minimum overhead to crowdsourcing workers.
-% TO mi prijde ze v call -centrech delaji stejne\OD{, apart from stating their replies in natural language (?)}
-The collected dialogues are published under Creative Commons 4.0 BY-SA license and available for download \ODdel{at {\it anonymized}}.\OD{Napsal bych radši do footnotu “URL will be provided in the camera-ready version of the paper”).}  % lindat\footnote{todo where}.
+The collected dialogues are published under Creative Commons 4.0 BY-SA license.\footnote{URL will be provided in the camera-ready version of the paper}  % lindat\footnote{todo where}.
 
@@
 
-\vspace{-1.40em}
-\subsubsection*{Acknowledgments}
-We would like to thank Ondřej Dušek for useful comments.
-This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333.\OD{Pro anonymizaci tuhle sekci zatím vynech.
-V plné verzi bys měl asi poděkovat i Lindatu.}
+% FIXME hidden for anonymised submission
+% \vspace{-1.40em}
+% \subsubsection*{Acknowledgments}
+% We would like to thank Ondřej Dušek for useful comments.
+% This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333.
+% It used language resources stored and distributed by the LINDAT/CLARIN project of the Ministry of Education, Youth and Sports of the Czech Repub- lic (project LM2015071).
 % We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.

### 2016-06-28 paper.tex
fix title
removed spaces in abstract
fixing worst paragraph

@@
 
-\title{A Dataset of Operator-client Dialogues Aligned with Database Queries for End-to-end training}
+\title{A Dataset of Operator-client Dialogues Aligned with Database Queries for End-to-end Training}
 
@@
 The dataset is collected using crowdsourcing and the conversations cover the well-known restaurant domain.
-    Quality of the data is enforced by mutual control among contributors.  % TODO and manually verified on random sub-sample 
+Quality of the data is enforced by mutual control among contributors.  
 The dataset is available for download under the Creative Commons 4.0 BY-SA license.
@@
 The task of building a conversational agents is traditionally simplified by creating pipeline of subtasks: each solved by specialised components: automatic speech recognition (ASR), language understanding (LU) unit, dialogue tracker (DT), dialogue manager (DM), natural language generator (NLG) and text-to-speech (TTS) module~\cite{duvsek2014alex}.
-The ASR~\cite{platek2014free} and TTS~\cite{taylor2009text} modules can be easily trained from data without understanding the meaning of the data and there are typically domain independent.
+The ASR~\cite{platek2014free} and TTS~\cite{taylor2009text} modules can be easily trained without understanding the meaning of the input and there are typically trained domain independently.
 The crucial task of conversation agents is to understand the dialogue history and respond with a reply which has the greatest expected benefit for the agent.
-The task of understanding and reply generation is traditionally solved by the text-to-text pipeline of LU, DT, DM, and NLG trained using just in-domain data~\cite{gasic2011line,jurvcivcek2014factored,duvsek2016sequence} annotated at level of each component.
-Our datasets provides just the textual input-output transcriptions of in~domain conversations and simple annotations in form of database calls.
-We expect that supervised models will be able model the meaning of the history and select its reply only from the transcriptions and the annotation.
+The task of understanding and reply generation is traditionally solved by the text-to-text pipeline of LU, DT, DM, and NLG components trained using just in-domain data which are annotated for each component~\cite{gasic2011line,jurvcivcek2014factored,duvsek2016sequence}.
+Our datasets contains just the textual transcriptions of input from client and output of the operator from indomain conversations and in addition it includes simple annotations in form of database calls.
+We expect that supervised models will be able to model the meaning of the history and select a~convenient reply only from the transcriptions and the annotations.
 

### 2016-06-28 paper.tex
further fixes

@@
 Multiple constrains can be expressed by two substrings separated by a comma.
-The content of the database is intentionally hidden if no filter is specified so that a filter has to be used to provide results.
+The content of the database is intentionally hidden.
+If no filter value is specified, the operator does not see content of the database so the filter has to be used to answer clients questions.
 The CF workers are also instructed to explicitly mark the database rows to which they refer in their answer.
@@
 The conversations are typically rather short circa four turns and therefore, full dialogues are collected after few rounds of submissions.
-The workers are paid  the same amount of money for every submitted response regardless of whether they play the client or the operator role.
+The workers are paid  the same amount of money for every submitted response regardless of dialogue history length and whether they play the client or the operator role.
 
@@
 There are two reason why there is more goals requested than answered.
-We saw a rare case when the goal was actually answered, but was not left marked as unanswered.
-However, much more common case is that the client asks for several goals e.g. phone and address, but he is satisfied if the operator provides just one of the goals e.g. phone. 
+We saw a rare case when the goal was actually answered, but was left marked as unanswered.
+However, more common case is that the client asks for several goals e.g. phone and address, but he is satisfied if the operator provides just one of the goals e.g. phone. 
 % Typically in \OP{65} \% case the conversation is ended by the client.
@@
 % \end{table}
+
 During the data collection process we discarded around \OP{35} \% of replies so far because the utterances were of low quality.

### 2016-06-29 paper.tex
minor fix

@@
 The operator CF worker is asked to politely address the clients needs according to the information stored in the database.
-In order to provide the information to clients, the operator uses the simple database interface depicted in~Figure~\ref{fig:operator}:
+In order to provide the information to clients, the operators use the simple database interface depicted in~Figure~\ref{fig:operator}:
 They filter the restaurants using a full text search over the database.

### 2016-08-02 paper.tex
minor fixes

@@
 We present a new dataset of human-human task-oriented conversations in the restaurant information domain, suitable for supervised training of autonomous systems. 
-We are currently collecting data for the set using crowdsourcing.
-We have collected 62 dialogues so far; more than 700 dialogues are planned for the final version of the dataset.\footnote{We expect to release the set before the camera-ready deadline.}
+We are currently collecting data for the set using crowdsourcing. We have collected 62 dialogues so far; more than 700 dialogues are planned for the final version of the dataset.
+% \footnote{We expect to release the set before the camera-ready deadline.}
 
@@
 The goals are displayed to the CF worker in the client role gradually turn-by-turn and may contradict each other.
-For example, the client may at first want a to find a restaurant serving Chinese food, but later change their mind and seek British food.
+For example, the client may at first attempts to find a restaurant serving Chinese food, but later change their mind and seeks British food.
 

### 2016-08-03 paper.tex
final version

@@
 
-\iftrue % FIXME uncomment for final submission
-\author{Firstname Lastname \and Firstname Lastname }
-\institute{
-Insitute\\
-\email{anonym@anonymous}
-}
-\fi
+% % \iftrue % FIXME uncomment for final submission
+% \author{Firstname Lastname \and Firstname Lastname }
+% \institute{
+% Insitute\\
+% \email{anonym@anonymous}
+% }
+% \fi
 
@@
 We are currently collecting data for the set using crowdsourcing. We have collected 62 dialogues so far; more than 700 dialogues are planned for the final version of the dataset.
-% \footnote{We expect to release the set before the camera-ready deadline.}
+\footnote{See the dataset at \url{http://hdl.handle.net/11234/1756}.}
 
@@
 We also introduced a novel data collection setting which resembles work of operators in call centers and introduces minimum overhead to crowdsourcing workers.
-The collected dialogues are published under Creative Commons 4.0 BY-SA license.\footnote{URL will be provided in the camera-ready version of the paper}  % lindat\footnote{todo where}.
+The collected dialogues are published under Creative Commons 4.0 BY-SA license.
 
@@
 
-% FIXME hidden for anonymised submission
-% \vspace{-1.40em}
-% \subsubsection*{Acknowledgments}
-% We would like to thank Ondřej Dušek for useful comments.
-% This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333.
-% It used language resources stored and distributed by the LINDAT/CLARIN project of the Ministry of Education, Youth and Sports of the Czech Repub- lic (project LM2015071).
-% We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.
-% Cloud computational resources were provided by the MetaCentrum under the program LM2010005 and the CERIT-SC under the program Center CERIT Scientific Cloud, part of the Operational Program Research and Development for Innovations, Reg.\ no.
+\vspace{-1.40em}
+\subsubsection*{Acknowledgments}
+We would like to thank Ondřej Dušek for useful comments.
+This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333.
+It used language resources stored and distributed by the LINDAT/CLARIN project of the Ministry of Education, Youth and Sports of the Czech Repub- lic (project LM2015071).
+We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.
+Cloud computational resources were provided by the MetaCentrum under the program LM2010005 and the CERIT-SC under the program Center CERIT Scientific Cloud, part of the Operational Program Research and Development for Innovations, Reg.\ no.
 CZ.1.05/3.2.00/08.0144.
